---
title: "Estimate posteriors including NCI-60"
author: "Matt Ploenzke"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimate concordance}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Set up and load packages.
```{r setup, include=FALSE}
  rm(list=ls(all=TRUE))
  knitr::opts_chunk$set(echo = TRUE)
  library(PharmacoMixtuR)
  library(tidyverse)
  library(ggridges)
  library(magrittr)
```

Set options.
```{r}
  opt <- list()
  opt$datasets <- c('CTRP','GDSC', 'NCI60') # GDSC CTRP  NCI60
  #opt$datasets <- c('CCLE','GDSC1000', 'gCSI', 'FIMM', 'CTRPv2') # CCLE GDSC GDSC1000 gCSI FIMM CTRPv2
  #opt$biomarkers_file <- '~/Desktop/Concordance/PSets/gene_drug_asociations.xlsx'
  opt$min_intersection <- 2 # Minimum number of studies a drug/cell must be assayed in to be included in the intersection comparison
  opt$log_dir <- paste(paste(opt$datasets,collapse='_'),'fit',sep='_')
  opt$sensitivity_measure <- c('ic50') # raw_auc e_inf hill_slope ec50 auc_recomputed
  # Prior specifications denoting cell sensitivity and proportion of drugs broadly-active:
  opt$prior.broadly.active <- 'median_mad' #median .05 # prior specification denoting drug is broadly-active if probability cell is sensitive is greater than value
  opt$run_on_cluster <- TRUE # this just changes file paths depending on where the code is being run
```

Set up log directory.
```{r}
  dir.create(opt$log_dir,showWarnings = FALSE)
  capture.output(opt, file = file.path(opt$log_dir,'model_Opts.csv'))
  basepath <- ifelse(opt$run_on_cluster,'PSets','../PSets')
```

Load intersection data pulled from https://discover.nci.nih.gov/cellminercdb/.
```{r}
CTRP_GDSC <- tibble()
for (file in list.files(file.path(basepath,'cellminer/CTRP_GDSC'), full.names = FALSE)) {
  tdat <- read.delim(file.path(basepath, 'cellminer/CTRP_GDSC',file)) %>% as_tibble()
  colnames(tdat)[2:3] <- c('CTRP','GDSC')
  CTRP_GDSC <- CTRP_GDSC %>% 
    bind_rows(tdat %>% 
                mutate(drug_code = gsub('.txt','',file)))
}

CTRP_NCI60 <- tibble()
for (file in list.files(file.path(basepath,'cellminer/CTRP_NCI60'), full.names = FALSE)) {
  tdat <- read.delim(file.path(basepath,'cellminer/CTRP_NCI60',file)) %>% as_tibble()
  colnames(tdat)[2:3] <- c('CTRP','NCI60')
  CTRP_NCI60 <- CTRP_NCI60 %>% 
    bind_rows(tdat %>% 
                mutate(drug_code = gsub('.txt','',file)))
}

GDSC_NCI60 <- tibble()
for (file in list.files(file.path(basepath,'cellminer/GDSC_NCI60'), full.names = FALSE)) {
  tdat <- read.delim(file.path(basepath, 'cellminer/GDSC_NCI60',file)) %>% as_tibble()
  colnames(tdat)[2:3] <- c('GDSC','NCI60')
  GDSC_NCI60 <- GDSC_NCI60 %>% 
    bind_rows(tdat %>% 
                mutate(drug_code = gsub('.txt','',file)))
}
```

Load NCI-60 full dataset.
```{r, eval=FALSE}
library(rcellminer)
library(readxl)
tdat <- exprs(getAct(rcellminerData::drugData)) %>%
  as.data.frame() %>%
  rownames_to_column('NSC') %>% 
  as_tibble()
mmc3 <- read_excel(file.path(basepath,"mmc3.xlsx"), range = "A5:G24") %>% as_tibble() # figure s6 cellminercdb paper
colnames(mmc3) <- c('drug','NSC','MOA','pearson','pearson_p', 'spearman','spearman_p')
nci60 <- tdat %>% 
  #right_join(mmc3, by='NSC') %>% 
  select(-NSC, -MOA, -pearson, -pearson_p, -spearman, -spearman_p) %>%
  pivot_longer(-drug, names_to='cell', values_to='value') %>%
  mutate(experiment = 'NCI60', measure=opt$sensitivity_measure) %>%
  select(drug, cell, value, experiment, measure) %>%
  na.omit()
```

Load drug name concordance.
```{r}
library(readxl)
drug_names <- read_excel(file.path(basepath,"mmc3.xlsx"), sheet='Sheet1') %>% # used cellminer to mannualy search for terms
  as_tibble() %>%
  pivot_longer(-drug,names_to='code', values_to = 'drug_code') %>% 
  select(-code) %>% 
  na.omit() %>% 
  mutate(drug_code = as.character(drug_code))
```

Format intersection data and drug names.
```{r}
GDSC_NCI60 %<>%
  select(Cell.Line, GDSC, NCI60, drug_code) %>%
  pivot_longer(cols = c('GDSC','NCI60'),names_to = 'experiment',values_to = 'value') %>%
  na.omit() %>%
  rename(cell = Cell.Line) %>%
  mutate(measure = opt$sensitivity_measure) %>%
  left_join(drug_names, by='drug_code') %>%
  select(-drug_code) %>%
  select(drug, cell, value, experiment, measure) %>%
  filter(is.finite(value) & !is.nan(value) & !is.na(value))

CTRP_NCI60 %<>%
  select(Cell.Line, CTRP, NCI60, drug_code) %>%
  pivot_longer(cols = c('CTRP','NCI60'),names_to = 'experiment',values_to = 'value') %>%
  na.omit() %>%
  rename(cell = Cell.Line) %>%
  mutate(measure = opt$sensitivity_measure) %>%
  left_join(drug_names, by='drug_code') %>%
  select(-drug_code) %>%
  select(drug, cell, value, experiment, measure) %>%
  filter(is.finite(value) & !is.nan(value) & !is.na(value))

CTRP_GDSC %<>%
  select(Cell.Line, CTRP, GDSC, drug_code) %>%
  pivot_longer(cols = c('CTRP','GDSC'),names_to = 'experiment',values_to = 'value') %>%
  na.omit() %>%
  rename(cell = Cell.Line) %>%
  mutate(measure = opt$sensitivity_measure) %>%
  left_join(drug_names, by='drug_code') %>%
  select(-drug_code) %>%
  select(drug, cell, value, experiment, measure) %>%
  filter(is.finite(value) & !is.nan(value) & !is.na(value))
```

Format the sensitivity data for each experiment.
```{r}
CTRP <- CTRP_GDSC %>% 
  bind_rows(CTRP_NCI60) %>% 
  filter(experiment=='CTRP') %>%
  distinct()
GDSC <- CTRP_GDSC %>% 
  bind_rows(GDSC_NCI60) %>% 
  filter(experiment=='GDSC') %>%
  distinct()
NCI60 <- CTRP_NCI60 %>% 
  bind_rows(GDSC_NCI60) %>% 
  filter(experiment=='NCI60') %>%
  distinct() 
sensitivity.tibble.list <- list(CTRP=CTRP, GDSC=GDSC, NCI60=NCI60)
```

Repeat but for the intersection.
```{r}
  intersection.tibble.list <- list(CTRP_GDSC = CTRP_GDSC,
                                   CTRP_NCI60 = CTRP_NCI60,
                                   GDSC_NCI60 = GDSC_NCI60)

  intersection.tibble.list <- lapply(intersection.tibble.list, function(ii) {
    ii %>% group_by(drug,measure) %>% filter(n_distinct(experiment) >= opt$min_intersection) %>% ungroup()
  })
```

Plot the distribution of each measure for the intersection.
```{r}
  for (meas in opt$sensitivity_measure) {
    dir.create(file.path(opt$log_dir,meas),showWarnings = FALSE)
    for (comp in names(intersection.tibble.list)) {
      dir.create(file.path(opt$log_dir,meas,comp),showWarnings = FALSE)
      p <- intersection.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        ggplot(aes(value)) +
          stat_bin(bins=50) + 
          theme_bw() + 
          facet_grid(cols = vars(experiment),rows=vars(drug), scales = 'free_y') + 
          theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +  
        theme(strip.text.x = element_text(size = 8), legend.position="none") + 
          scale_x_continuous(name = meas) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('densities_raw.pdf',sep='')),width = 12, height = 24, units = "in")
      saveRDS(p, file.path(opt$log_dir,meas,comp,paste('densities_raw.RDS',sep='')))
      p <- intersection.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(x=value,y=drug,fill=experiment)) +
        geom_density_ridges(alpha = .2) + 
        #scale_x_continuous(limits = c(0,1)) + 
        theme_bw() +  scale_fill_brewer(palette="Dark2") +
        theme(axis.title.y = element_blank()) + 
        theme(strip.text.x = element_text(size = 24),
              legend.text=element_text(size=24),
              legend.title=element_text(size=24),
              legend.position="top",
              axis.text=element_text(size=24),
              axis.title = element_text(size=24),
              plot.title = element_text(size = 42),
              plot.subtitle = element_text(size = 32)) +
        labs(x='AAC',title='CCLE and GDSC sensitivity distributions', subtitle= 'Only common drugs shown')
        ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('smoothed_densities_raw.png',sep='')),width = 16, height = 26, units = "in")
        saveRDS(p, file = file.path(opt$log_dir,meas,comp,paste('smoothed_densities_raw.RDS',sep='')))
    }
   p <- intersection.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug)) +
          geom_boxplot() + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position='none',
            axis.text=element_text(size=16),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            scale_y_continuous(breaks=c(0,1)) +
            labs(x="Drug",y=meas)
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_common_drugs.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file.path(opt$log_dir,meas,comp,paste('boxplot_raw_common_drugs.RDS',sep='')))
  }
  while(dev.cur()!=1) {dev.off()}
  common.drugs <- lapply(names(intersection.tibble.list), function(comp) {
    intersection.tibble.list[[comp]] %>%
      distinct(drug) %>% 
      pull()
  })
  names(common.drugs) <- names(intersection.tibble.list)
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      p <- sensitivity.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug,fill=experiment)) +
          geom_boxplot() + 
          theme_bw() + 
          #facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.text.y=element_text(size=16),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            scale_y_continuous(breaks=c(0,1)) +
            labs(x="Drug",y=NULL)
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells.RDS',sep='')))
      maxdr <- sensitivity.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        summarise(max(nchar(drug))) %>%
        pull()
      p <- sensitivity.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas) %>%
        mutate(color = ifelse(drug %in% common.drugs[[comp]],'blue','grey')) %>%
        mutate(drug=as.factor(drug),color=as.factor(color)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug)) +
          geom_boxplot(aes(color=color),show.legend=FALSE) + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='none',
            axis.text=element_text(size=16),
            axis.text.x =element_text(colour = 'white',angle = 45, hjust = 1,size=8),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            labs(x="Drug",y='AAC', title=comp) + 
            scale_y_continuous(breaks=c(0,1)) +
            scale_color_manual(values=c('black','grey50')) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs.png',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs.RDS',sep='')))
    }
  }
```

Boxplot of all cells.
```{r}
p <- sensitivity.tibble.list[['CTRP']] %>%
  bind_rows(sensitivity.tibble.list[['GDSC']]) %>% 
  bind_rows(sensitivity.tibble.list[['NCI60']]) %>% 
  group_by(drug) %>%
  mutate(numm = n_distinct(experiment)) %>%
  ungroup() %>%
  filter(numm >= 2) %>%
  mutate(drug=reorder(drug, value, median)) %>%
  ggplot(aes(x=drug,y=value,fill=experiment)) + 
  geom_boxplot() +  
  theme_bw() + 
  scale_fill_brewer(palette='Dark2') +
  theme(legend.position='bottom',
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x='',y='IC50',subtitle='Only common drugs shown',fill='',title='Sensitivity distributions')
ggsave(p,file=file.path(opt$log_dir,meas,paste('boxplot_raw_common_drugs.png',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
saveRDS(p, file=file.path(opt$log_dir,meas,paste('boxplot_raw_commons_drugs.RDS',sep='')))
```

Repeat for individual studies.
```{r}
  for (meas in opt$sensitivity_measure) {
    dir.create(file.path(opt$log_dir,meas),showWarnings = FALSE)
    for (comp in names(sensitivity.tibble.list)) {
      dir.create(file.path(opt$log_dir,meas,comp),showWarnings = FALSE)
      num_drug <- length(unique(sensitivity.tibble.list[[comp]]$drug))
      p <- sensitivity.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        ggplot(aes(value)) +
          stat_bin(bins=50) + 
          theme_bw() + 
          facet_wrap(vars(drug), scales = 'free_y',ncol=3) + 
            theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +
          #coord_cartesian(xlim = c(0, 1)) +
          scale_x_continuous(name = meas) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('densities_raw.pdf',sep='')),width = 12, height = num_drug, units = "in",limitsize=FALSE)
      saveRDS(p,file=file.path(opt$log_dir,meas,comp,paste('densities_raw.RDS',sep='')))
      while(dev.cur()!=1) {dev.off()}
      p <- sensitivity.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(drug=reorder(drug, value, median)) %>%
        ggplot(aes(x=drug,y=value)) +
          geom_boxplot() + 
          theme_bw() + 
            theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
          #coord_cartesian(ylim = c(0, 1)) +
          labs(x='Compound',y='sensitivity',title=comp)
      if (comp %in% c('GDSC','CTRPv2')) {
        p <- p + theme(axis.text.x =element_blank())
      }
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplots_raw.png',sep='')),width = 12, height=6, units = "in")
      saveRDS(p,file=file.path(opt$log_dir,meas,comp,paste('boxplots_raw.RDS',sep='')))
    }
  }
  while(dev.cur()!=1) {dev.off()}
```

Plot the pairwise concordance between two studies at a time.
```{r}
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      combos <- t(combn(sort(unique(intersection.tibble.list[[comp]]$experiment)),2))
      for (combo in 1:nrow(combos)) {
        p <- intersection.tibble.list[[comp]] %>%
          filter(experiment %in% combos[combo,],
                 measure == meas) %>%
          select(drug,cell,experiment, measure, everything()) %>%
          gather(variable, value, -(drug:measure)) %>% 
          unite(temp, experiment, variable) %>%
          spread(temp,value) %>%
          ggplot(aes_string(x=paste(combos[combo,1],'value',sep='_'),
                            y=paste(combos[combo,2],'value',sep='_'))) + 
          geom_point(alpha=.15,size=1.5) + 
          scale_color_brewer(palette = 'Dark2') + 
          geom_abline(slope=1, size=.5,color='black', lty=3) + 
          theme_bw() + 
          facet_wrap(vars(drug),ncol=5) + 
          theme(strip.text.x = element_text(size = 12),
            legend.position='top',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=0),
            title=element_text(size=14)) +
          labs(x=combos[combo,1], y=combos[combo,2]) #+ 
          #scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1)) +
          #scale_y_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1))
        ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('2way_',
                                              combos[combo,1],'_',combos[combo,2],
                                              '.pdf',sep='')),
             width = 18, height = 10, units = "in")
        saveRDS(p,file=file.path(opt$log_dir,meas,comp,paste('2way_',
                                              combos[combo,1],'_',combos[combo,2],
                                              '.RDS',sep='')))
        drugs <- unique(intersection.tibble.list[[comp]]$drug)
        dir.create(file.path(opt$log_dir,meas,comp,'by_drug'),showWarnings = FALSE)
        for (dr in drugs) {
          p <- intersection.tibble.list[[comp]] %>%
          filter(experiment %in% combos[combo,],drug==dr,measure==meas) %>% 
          select(drug,cell,experiment, measure, everything()) %>%
          gather(variable, value, -(drug:measure)) %>% 
          unite(temp, experiment, variable) %>%
          spread(temp,value) %>%
          #mutate(CCLE_value = (CCLE_value-mean(CCLE_value))/sd(CCLE_value),
          #       GDSC_value = (GDSC_value-mean(GDSC_value))/sd(GDSC_value)) %>%
          ggplot(aes_string(x=paste(combos[combo,1],'value',sep='_'),
                            y=paste(combos[combo,2],'value',sep='_'))) + 
          geom_point(alpha=.5,size=4) + 
          #geom_smooth(method='lm',se=FALSE) +
          scale_color_brewer(palette = 'Dark2') + 
          theme_bw() + 
          theme(strip.text.x = element_text(size = 12),
              legend.position='top',
              axis.text=element_text(size=16),
              axis.title=element_text(size=16),
              legend.text=element_text(size=22),
              legend.title=element_text(size=0),
              title=element_text(size=14)) +
          labs(x=combos[combo,1],y=combos[combo,2],title=paste(dr,' common cell sensitivity (AAC)',sep='')) #+ 
          #scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1)) +
          #scale_y_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1))
        ggsave(p,file=file.path(opt$log_dir,meas,comp,'by_drug',paste(dr,'_2way_',
                                                combos[combo,1],'_',combos[combo,2],
                                                '.png',sep='')),
               width = 10, height = 8, units = "in")
        saveRDS(p,file.path(opt$log_dir,meas,comp,'by_drug',paste(dr,'_2way_',
                                                combos[combo,1],'_',combos[combo,2],
                                                '.RDS',sep='')))
        }
      }
    }
  }
```

Remove PSets.
```{r}
rm(GDSC, CTRP, NCI60, CTRP_NCI60, GDSC_NCI60, CTRP_GDSC)
```

Initialize drug and cell assignments for EM using prior specifications for probability sensitive and probability drug is broadly active.
```{r}
NCI60_prior_median <- .6
ctrp_prior_median <- .65
gdsc_prior_median <- .7
NCI60_prior_mad <- .7
ctrp_prior_mad <- .7
gdsc_prior_mad <- .7
drugs.tibble.list <- lapply(sensitivity.tibble.list, function(li) {
  drug_dat <- li %>% 
    mutate(all_median = case_when(experiment=='NCI60'  ~ quantile(value, NCI60_prior_median),
                                  experiment=='CTRP'  ~ quantile(value, ctrp_prior_median),
                                  experiment=='GDSC'  ~ quantile(value, gdsc_prior_median),
                                  TRUE ~ quantile(value,.6)),
           drug=as.factor(drug)) %>% 
    group_by(drug) %>% 
    mutate(median=median(value),
           mad = quantile(abs(value-median(value)), .5),
           all_median=first(all_median),
           experiment = first(experiment)) %>%
    ungroup() %>%
    mutate(all_mad=case_when(experiment=='NCI60'  ~ quantile(mad, NCI60_prior_mad),
                             experiment=='CTRP'  ~ quantile(mad, ctrp_prior_mad),
                             experiment=='GDSC'  ~ quantile(mad, gdsc_prior_mad),
                             TRUE ~ quantile(mad, .5)),
           drug_type = ifelse(median<=all_median & mad<=all_mad,'targeted','broad')) %>%
    distinct(drug, drug_type, all_median, all_mad, median, mad)
  li %>% 
    left_join(drug_dat, by='drug') %>%
    mutate(thhreshold = case_when(#experiment=='NCI60' ~ (1-(mad/max(mad)))*.25,
                                  experiment=='NCI60' & drug_type=='targeted' ~ median+1.25,
                                  experiment=='NCI60' & drug_type=='broad' ~ -.25,
                                  experiment=='CTRP' ~ 20,
                                  experiment=='GDSC' ~ all_median,
                                  TRUE ~ 0)) %>%
    group_by(drug) %>%
    mutate(sensitive = as.numeric(value >= thhreshold)) %>%
    ungroup() %>%
    group_by(drug, measure, drug_type, thhreshold) %>%
    summarise(p_prior = mean(sensitive),
              sensitive = sum(sensitive),
              cell_count = n()) %>%
    ungroup() %>% 
    rename(prior_threshold = thhreshold) %>%
    select(drug, measure, p_prior, sensitive, cell_count, drug_type, prior_threshold)
})
cells.tibble.list <- lapply(1:length(sensitivity.tibble.list), function(li) {
  sensitivity.tibble.list[[li]] %>% 
    left_join(drugs.tibble.list[[li]], by=c('drug','measure')) %>% 
    select(drug:measure,drug_type, prior_threshold) %>%
    ungroup() %>% 
    group_by(experiment) %>%
    mutate(cell_type = ifelse(value >= prior_threshold,'sensitive','resistant')) %>%
    ungroup()
})
names(cells.tibble.list) <- names(drugs.tibble.list)
```

Plot median versus median absolute deviation for joined data using the MAD and specified percentile for drug-type classification.
```{r}
library(ggrepel)
  for (meas in opt$sensitivity_measure) {
    for (comp in names(sensitivity.tibble.list)) {
      p <- sensitivity.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(all_median = case_when(experiment=='NCI60'  ~ quantile(value, NCI60_prior_median),
                                  experiment=='CTRP'  ~ quantile(value, ctrp_prior_median),
                                  experiment=='GDSC'  ~ quantile(value, gdsc_prior_median),
                                  TRUE ~ quantile(value,.6)),
               drug=as.factor(drug)) %>% 
        group_by(drug) %>% 
        summarise(median=median(value),
               mad = quantile(abs(value-median(value)), .5),
               all_median=first(all_median),
               experiment = first(experiment)) %>%
        ungroup() %>%
        mutate(all_mad=case_when(experiment=='NCI60'  ~ quantile(mad, NCI60_prior_mad),
                                 experiment=='CTRP'  ~ quantile(mad, ctrp_prior_mad),
                                 experiment=='GDSC'  ~ quantile(mad, gdsc_prior_mad),
                                 TRUE ~ quantile(mad, .5)),
               broad = ifelse(median<=all_median & mad<=all_mad,'Narrow effect','Broad effect'),
               broad_hk = ifelse(mad>.13,'Broad effect','Narrow effect')) %>%
        ggplot(aes(x=median,y=mad)) + 
        geom_point(aes(color=broad),size=4,alpha=.6,show.legend=FALSE) +
        #geom_label_repel(aes(label=drug)) +
        #geom_hline(aes(yintercept=.13),lty=2,color=2) + 
        geom_hline(aes(yintercept=all_mad),lty=2) + 
        geom_vline(aes(xintercept=all_median),lty=2) +
        theme_bw() +
        labs(x='Median AAC', y='Median absolute deviation (MAD)') + 
        ggtitle(comp)
      ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD.pdf',sep='')),width = 5, height = 5, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD.RDS',sep='')))
    }
  }
```

Smoothed density of the prior pi across all studies.
```{r}
  for (meas in opt$sensitivity_measure) {
    temptibb <- tibble()
    for (comp in names(sensitivity.tibble.list)) {
      temptibb <- drugs.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(experiment=comp) %>%
        bind_rows(temptibb)
    }
    p <- temptibb %>% 
      ggplot(aes(x=p_prior,fill='one',y=..scaled..)) +
        geom_density(alpha = .5) + 
        theme_bw() +  
        facet_wrap(vars(experiment),nrow=2) +
        scale_fill_brewer(palette="Dark2") +
        theme(strip.text.x = element_text(size = 14),
              legend.text=element_text(size=14),
              legend.title=element_text(size=14),
              legend.position="none",
              axis.text=element_text(size=12),
              axis.title = element_text(size=14),
              plot.title = element_text(size = 16)) +
        scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1),name=expression(paste(p, '(',pi, ")",sep=''))) +
        scale_y_continuous(breaks=c(0,1),labels=c('0','1'),limits = c(0,1), name='Density')
    ggsave(p, file=file.path(opt$log_dir,meas,paste('p_prior_smoothed.pdf',sep='')),width = 4, height = 4, units = "in",limitsize=FALSE)
    saveRDS(p, file=file.path(opt$log_dir,meas,paste('p_prior_smoothed.RDS',sep='')))
  }
```

Using the assignments, fit distributions (first M step) and use these as priors to initialize EM with. 
```{r}
meas <- opt$sensitivity_measure
drug_types_list <- lapply(drugs.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    group_by(drug_type) %>%
    do(mutate(fit_bb_mle(.$sensitive, .$cell_count), number = nrow(.))) %>%
    ungroup() %>%
    mutate(drug_type_prior = number / sum(number))
})
targetted_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  ttibb <- tibb %>%
    filter(measure==meas) %>%
    mutate(drug_type = 'targeted') %>%
    group_by(drug, cell_type, drug_type, experiment) %>%
    do(mutate(fit_normal_mle(.$value),number = nrow(.))) %>%
    group_by(drug, drug_type, experiment) %>%
    mutate(ndist=n_distinct(cell_type)) %>%
    ungroup()
  ttibb %>%
    bind_rows(
      ttibb %>% 
        filter(ndist<2) %>% 
        mutate(cell_type2 = case_when(cell_type=='resistant' ~ 'sensitive',cell_type=='sensitive' ~ 'resistant'),
               cell_type=cell_type2,
               number=0,
               mu=case_when(cell_type == 'resistant' ~ 0,
                               cell_type == 'sensitive' ~ 5),
               sigma=case_when(cell_type == 'resistant' ~ 1,
                              cell_type == 'sensitive' ~ 1)) %>%
        select(-cell_type2)
    ) %>%
    group_by(drug, experiment) %>%       
    mutate(targeted_cell_type_prior = number / sum(number)) %>%
    mutate(targeted_cell_type_prior = pmax(pmin(targeted_cell_type_prior, .99),.01)) %>%
    ungroup() %>% 
    select(-ndist)
})
broad_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    group_by(drug, experiment) %>%
    do(mutate(fit_normal_mle(.$value),
              number = nrow(.),
              broad_cell_type_prior = mean(.$value>=.$prior_threshold))) %>%
    ungroup() %>% 
    mutate(drug_type = 'broad') %>%
    mutate(broad_cell_type_prior = pmax(pmin(broad_cell_type_prior, .99),.01)) %>%
    select(drug, drug_type, mu, sigma, number, broad_cell_type_prior, experiment)
})
targeted_drug_priors <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_fits_list[[num]] %>% 
    rename(cell_type_prior = targeted_cell_type_prior) %>%
    select(drug, drug_type, cell_type_prior, experiment, cell_type) %>%
    mutate(drug_type = 'broad')
})
broad_drug_priors <- lapply(1:length(broad_drug_fits_list), function(num) {
  broad_drug_fits_list[[num]] %>%
    rename(cell_type_prior = broad_cell_type_prior) %>%
    select(drug, drug_type, cell_type_prior, experiment) %>%
    mutate(drug_type = 'targeted')
})
```

Perform an expectation step using the distributions to initialize for the EM. 
```{r}
targetted_cell_assignments_list <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_list <- unique(targetted_drug_fits_list[[num]]$drug)
  targetted_cell_assignments <- lapply(targetted_drug_list, function(dr) {
    cells.tibble.list[[num]] %>%
      filter(drug == dr,measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'targeted') %>%
      crossing(targetted_drug_fits_list[[num]] %>% filter(drug == dr) %>% select(-drug,-drug_type) %>% rename(experiment1=experiment)) %>%
      filter(experiment==experiment1) %>% 
      select(-experiment1) %>% 
      mutate(median = qnorm(.5,mu,sigma),
             likelihood = dnorm(value, mu, sigma)) %>% 
      group_by(cell_type) %>%
      mutate(max.likelihood=max(likelihood)) %>%
      ungroup() %>%
      mutate(likelihood = case_when(value>median & cell_type == 'sensitive' ~ max.likelihood-likelihood + max.likelihood, 
                                    value<median & cell_type == 'resistant' ~ max.likelihood-likelihood + max.likelihood, 
                                    TRUE~likelihood)) %>%
      mutate(likelihood = targeted_cell_type_prior * likelihood) %>%
      group_by(drug, cell, experiment) %>%
      mutate(posterior=exp(log(likelihood)-log(sum(likelihood)))) %>% 
      top_n(1, likelihood) %>%
      ungroup()
  })
  do.call(bind_rows, targetted_cell_assignments)
})
broad_cell_assignments_list <- lapply(1:length(broad_drug_fits_list), function(num) {
  cells.tibble.list[[num]] %>%
      filter(drug %in% unique(broad_drug_fits_list[[num]]$drug),measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'broad') %>%
      left_join(broad_drug_fits_list[[num]], by=c('drug','drug_type', 'experiment')) %>%
      mutate(likelihood = dnorm(value, mu, sigma),
             cell_type = ifelse((broad_cell_type_prior*pnorm(value, mu, sigma)) >
                                ((1-broad_cell_type_prior)*(1-pnorm(value, mu, sigma))),
                              'sensitive','resistant'))
})

drugs.tibble.list <- lapply(1:length(drugs.tibble.list), function(num) {
  targetteds <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(targetted_cell_assignments_list[[num]] %>% select(drug, cell, cell_type, likelihood), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>% 
    mutate(type='targeted')
  broads <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(broad_cell_assignments_list[[num]] %>% select(drug, cell, cell_type), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>%
    mutate(type='broad')
  bind_rows(targetteds, broads)
})

drug_assignments_list <- lapply(1:length(drugs.tibble.list), function(num) {
  drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    rename(drug_type = type) %>%
    right_join(drug_types_list[[num]] %>% select(-number), by='drug_type') %>%
    mutate(likelihood = drug_type_prior * VGAM::dbetabinom.ab(sensitive, cell_count, alpha, beta)) %>%
    group_by(drug) %>%
    mutate(posterior=likelihood/sum(likelihood)) %>% 
    top_n(1, likelihood) %>%
    ungroup()
})

cell_assignments_list <- lapply(1:length(targetted_cell_assignments_list), function(num) {
  bind_rows(targetted_cell_assignments_list[[num]],broad_cell_assignments_list[[num]]) %>%
    left_join(targeted_drug_priors[[num]], by=c('drug','experiment','drug_type','cell_type')) %>%
    mutate(targeted_cell_type_prior = case_when(is.na(targeted_cell_type_prior) & drug_type=='broad' ~ cell_type_prior,
                                                TRUE ~ targeted_cell_type_prior)) %>%
    select(-cell_type_prior) %>%
    left_join(broad_drug_priors[[num]],  by=c('drug','experiment','drug_type')) %>%
    mutate(broad_cell_type_prior = case_when(is.na(broad_cell_type_prior) & drug_type=='targeted' ~ cell_type_prior,
                                                TRUE ~ broad_cell_type_prior)) %>%
    select(-cell_type_prior) %>%
    right_join(drug_assignments_list[[num]] %>% select(drug, drug_type), by=c('drug','drug_type')) %>% 
    select(drug, cell, value, experiment, measure, drug_type, cell_type, broad_cell_type_prior, targeted_cell_type_prior)
})
names(cell_assignments_list) <- names(drug_types_list)
```

Run EM.
```{r}
  iterations_list <- list()
  for(num in 1:length(cell_assignments_list)) {
    drug_assignments <- drug_assignments_list[[num]]
    cell_assignments <- cell_assignments_list[[num]]
    targeted_priors <- targeted_drug_priors[[num]]
    broad_priors <- broad_drug_priors[[num]]
    iterations_list[[num]] <- accumulate(1:25, iterate_normal_em, .init = list(drug_assignments = drug_assignments,
                                                                       cell_assignments = cell_assignments,
                                                                       targeted_priors = targeted_priors,
                                                                       broad_priors = broad_priors))
  }
  names(iterations_list) <- names(sensitivity.tibble.list)
```

Plot parameters across iterations.
```{r}
for (num in names(iterations_list)) {
  drug_type_iterations <- iterations_list[[num]] %>% 
    map_df("drug_types", .id = "iteration") %>% 
    bind_rows(drug_types_list[[num]] %>% 
                mutate(iteration='0')) %>%
    group_by(iteration) %>%
    mutate(drug_type_prior = case_when(is.na(drug_type_prior) ~ number/sum(number), TRUE ~ drug_type_prior)) %>%
    ungroup()
  drug_fits_iterations <- iterations_list[[num]] %>% 
    map_df("drug_fits", .id = "iteration") %>% 
    bind_rows(broad_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, mu, sigma, iteration),
              targetted_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, mu, sigma, iteration))
  cell_assignments_iterations <- iterations_list[[num]] %>% 
    map_df("cell_assignments", .id = "iteration") %>% 
    bind_rows(cell_assignments_list[[num]] %>%
                mutate(iteration='0'))
  p <- drug_type_iterations %>%
    crossing(x = seq(.001, .999, .001)) %>%
    mutate(density = drug_type_prior * dbeta(x, alpha, beta)) %>%
    ggplot(aes(x, density, color = iteration, group = iteration)) +
    geom_line() +
    facet_wrap(~ drug_type) + 
    theme(strip.text.x = element_text(size = 18),
          legend.position='bottom',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=16),
          title=element_text(size=18)) +
          labs(y='Density',x='AOC')
  ggsave(p,file=file.path(opt$log_dir,meas,num,paste('parameter_updates.pdf',sep='')),width = 12, height = 8, units = "in")
  saveRDS(p,file=file.path(opt$log_dir,meas,num,paste('parameter_updates.RDS',sep='')))
}
```

Obtain posterior information from last EM rep.
```{r}
  posterior_drug_types_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_types", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_assignments", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_fits_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_fits", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_cell_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("cell_assignments", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  names(posterior_cell_assignments_list) <- names(iterations_list)
```

Do one more rep.
```{r}
  posteriors_list <- list()
  for(num in 1:length(cell_assignments_list)) {
    drug_assignments <- posterior_drug_assignments_list[[num]] %>% select(-iteration)
    cell_assignments <- posterior_cell_assignments_list[[num]]  %>% select(-iteration)
    targeted_priors <- targeted_drug_priors[[num]]
    broad_priors <- broad_drug_priors[[num]]
    posteriors_list[[num]] <- accumulate(1, iterate_normal_em, .init = list(drug_assignments = drug_assignments,
                                                                 cell_assignments = cell_assignments,
                                                                  targeted_priors = targeted_priors,
                                                                       broad_priors = broad_priors),
                                         last=TRUE)
  }
  names(posteriors_list) <- names(sensitivity.tibble.list)
  
  posterior_drug_types_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("drug_types", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_assignments_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("drug_assignments", .id = "iteration") %>%
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_fits_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("drug_fits", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_cell_assignments_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("cell_assignments", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  names(posterior_cell_assignments_full) <- names(posteriors_list)
```

Plot the posterior drug densities.
```{r}  
drug_posteriors_proportions <- lapply(names(posterior_cell_assignments_list), function(ii) {
  posterior_cell_assignments_list[[ii]] %>%
    group_by(drug) %>%
    summarise(posterior = sum(cell_type=='sensitive')/n()) %>%
    ungroup()
}) 
names(drug_posteriors_proportions) <- names(iterations_list)
for (num in names(iterations_list)) {
  drug_type_iterations <- iterations_list[[num]] %>% 
    map_df("drug_types", .id = "iteration") %>% 
    bind_rows(drug_types_list[[num]] %>% 
                mutate(iteration='0')) %>%
    group_by(iteration) %>%
    mutate(drug_type_prior = case_when(is.na(drug_type_prior) ~ number/sum(number), TRUE ~ drug_type_prior)) %>%
    ungroup()
  if (num=='CTRP') {
    limms <- seq(5,30,by=.25)
  } else if (num=='GDSC') {
    limms <- seq(2.5,10,by=.05)
  } else if (num=='NCI60') {
    limms <- seq(-5,7.5,by=.05)
  } else {
    limms <- seq(-5,10,by=.05)
  }
  drug_fits_iterations <- iterations_list[[num]] %>% 
    map_df("drug_fits", .id = "iteration") %>% 
    bind_rows(broad_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, mu, sigma, iteration),
              targetted_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, mu, sigma, iteration))
  cell_assignments_iterations <- iterations_list[[num]] %>% 
    map_df("cell_assignments", .id = "iteration") %>% 
    bind_rows(cell_assignments_list[[num]] %>%
                mutate(iteration='0'))
  normaldens <- drug_fits_iterations %>%
    filter(iteration==max(iteration)) %>%
    mutate(cross = paste(cell_type, drug, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = limms,
      normal_curve = dnorm(limms, 
                           df$mu, 
                           df$sigma) 
    )
  })
  normaldens <- as_tibble(normaldens) %>% 
    separate(cross,into=c('cell_type','drug'),sep='_') %>%
    full_join(drug_fits_iterations %>% mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), by=c('drug','cell_type')) %>% 
    left_join(drug_posteriors_proportions[[num]], by='drug') %>%
    mutate(posterior = ifelse(drug_type=='broad',1,posterior)) %>%
    mutate(posterior = ifelse(drug_type=='targeted' & cell_type=='resistant',1,posterior)) %>%
    group_by(drug,cell_type) %>% 
    #mutate(prior = ifelse(prior < .1,.1,prior)) %>%
    mutate(normal_curve = normal_curve/max(normal_curve)*posterior) %>%
    ungroup() %>%
    filter(iteration==max(iteration)) %>%
    mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
  nummdrs <- normaldens %>% summarise(n_distinct(drug)) %>% pull()
  drs_array <- normaldens %>% distinct(drug) %>% pull()
  seeqq <- seq(1,nummdrs,by=16)
  for (dr_chunk in 1:length(seeqq)) {
    p <- cell_assignments_iterations %>%
      filter(iteration==max(iteration)) %>%
      filter(drug %in% drs_array[seeqq[dr_chunk]:(seeqq[dr_chunk]+15)]) %>%
      ggplot(aes(value,y=..scaled..)) +
        geom_density(adjust=.5,fill=1) +
        theme_bw() + 
        facet_wrap(vars(drug), scales = 'free_y',ncol=4) + 
        theme(strip.text.x = element_text(size = 8),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
      #scale_x_continuous(limits = c(0,1), name=meas) + 
      geom_line(data=normaldens %>% filter(drug %in% drs_array[seeqq[dr_chunk]:(seeqq[dr_chunk]+15)]), aes(y = normal_curve, color=cell_type), lwd = 1) 
    ggsave(p, file=file.path(opt$log_dir,meas,num,paste('fitted_densities_smoothed_',dr_chunk,'.pdf',sep='')),width = 12, height = 24, units = "in")
    saveRDS(p, file=file.path(opt$log_dir,meas,num,paste('fitted_densities_smoothed_',dr_chunk,'.RDS',sep='')))
    while(dev.cur()!=1) {dev.off()}
  }
  dir.create(file.path(opt$log_dir,meas,num,'fitted_densities_by_drug'),showWarnings = FALSE)
  for (dr in unique(cell_assignments_iterations$drug)) {
    dr_type <- cell_assignments_iterations %>%
      filter(iteration==max(iteration),drug==dr) %>% 
      distinct(drug_type) %>% 
      pull
    dr_short <- gsub("[^[:alnum:]]","",dr)
    dr_nonums <- gsub('[0-9]+', '', dr_short)
    if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
    p <- cell_assignments_iterations %>%
      filter(iteration==max(iteration),drug==dr) %>%
      ggplot(aes(value,y=..scaled..)) +
        geom_density(adjust=.5,fill=1) +
        theme_bw() + 
        theme(strip.text.x = element_text(size = 18),
          legend.position='none',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=16),
          title=element_text(size=18)) +
      #scale_x_continuous(limits = c(0,1)) + 
      labs(y='Scaled Density',x='sensitivity') +
      geom_line(data=normaldens %>% filter(drug==dr), aes(y = normal_curve, color=cell_type), lwd = 1.5) +
      ggtitle(paste(dr,sep=' '))
    ggsave(file=file.path(opt$log_dir,meas,num,'fitted_densities_by_drug',paste(dr_short,'.png',sep='')),width = 12, height = 4, units = "in")
    saveRDS(p, file.path(opt$log_dir,meas,num,'fitted_densities_by_drug',paste(dr_short,'.RDS',sep='')))
  }
}
```

Format posterior agreements.
```{r}
  posterior_drug_types <- do.call(bind_rows,posterior_drug_types_list) %>%
    mutate(experiment=rep(names(iterations_list),each=2)) 
  nums <- sapply(posterior_drug_assignments_list, nrow)
  posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  nums <- sapply(posterior_drug_fits_list, nrow)
  posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  nums <- sapply(posterior_cell_assignments_list, nrow)
  posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  
  posterior_drug_types <- do.call(bind_rows,posterior_drug_types_full) %>%
    mutate(experiment=rep(names(posteriors_list),each=2)) 
  nums <- sapply(posterior_drug_assignments_full, nrow)
  posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_full) %>%
      mutate(experiment=rep(names(posteriors_list),times=nums))
  nums <- sapply(posterior_drug_fits_full, nrow)
  posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_full) %>%
      mutate(experiment=rep(names(posteriors_list),times=nums))
  nums <- sapply(posterior_cell_assignments_full, nrow)
  posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_full) %>%
      mutate(experiment=rep(names(posteriors_list),times=nums))
```

Save posteriors.
```{r}
saveRDS(object=posterior_drug_types,file=file.path(opt$log_dir,'posterior_drug_types.RDS'))
saveRDS(object=posterior_drug_fits,file=file.path(opt$log_dir,'posterior_drug_fits.RDS'))
saveRDS(object=posterior_drug_assignments,file=file.path(opt$log_dir,'posterior_drug_assignments.RDS'))
saveRDS(object=posterior_cell_assignments,file=file.path(opt$log_dir,'posterior_cell_assignments.RDS'))
```

Format a big data frame with all relevant posterior information.
```{r}
posterior_cell_assignments <- readRDS(file=file.path(opt$log_dir,'posterior_cell_assignments.RDS'))
posterior_drug_assignments <- readRDS(file=file.path(opt$log_dir,'posterior_drug_assignments.RDS'))
posterior_drug_fits <- readRDS(file=file.path(opt$log_dir,'posterior_drug_fits.RDS'))

posterior <- posterior_cell_assignments %>%
  select(drug, cell, experiment, drug_type, cell_type, posterior, likelihood, value) %>%
  rename(cell_type_posterior=posterior,
         cell_type_likelihood=likelihood,
         realized_value=value) %>%
  group_by(drug, cell) %>% 
  mutate(num_experiments = n_distinct(experiment)) %>%
  ungroup() %>%
  left_join(posterior_drug_assignments %>%
              select(drug, drug_type, posterior,likelihood, experiment) %>%
              rename(drug_type_posterior=posterior,
                     drug_type_likelihood=likelihood), by=c('drug_type','drug','experiment')) %>%
  mutate(cell_type = ifelse(cell_type == 'sensitive' & drug_type == 'broad',
                            'resistant',cell_type)) %>%
  left_join(posterior_drug_fits %>%
              select(drug, cell_type, experiment, mu, sigma, drug_type),
            by = c('drug','cell_type','experiment','drug_type')) %>%
  mutate(cell_type_posterior = case_when(drug_type == 'broad' ~ pnorm(realized_value, mu, sigma, lower.tail = FALSE),
                                         TRUE ~ cell_type_posterior)) %>%
  select(-mu, -sigma) %>%
  mutate(cell_type_posterior = ifelse((cell_type == 'resistant' & drug_type == 'targeted') | drug_type=='broad',
                                      1-cell_type_posterior,cell_type_posterior)) %>%
  mutate(drug_type_posterior = ifelse(drug_type == 'broad', 1-drug_type_posterior,drug_type_posterior)) %>%
  rename(posterior_probability_sensitive = cell_type_posterior,
         posterior_probability_targeted = drug_type_posterior)
saveRDS(object=posterior,file=file.path(opt$log_dir,'posterior.formatted.RDS'))
```

Extract intersection data.
```{r}
  intersection.fitted.list <- lapply(intersection.tibble.list, function(tibb) {
    drugs_cells <- tibb %>% 
      distinct(drug,cell, experiment, measure, value) %>%
      rename(realized_value = value)
    experiments <- tibb %>% 
      distinct(experiment) %>%
      pull
    drugs_cells %>% 
      left_join(posterior %>% 
                  filter(experiment %in% experiments) %>%
                  select(drug, cell, experiment,
                         drug_type, posterior_probability_targeted, drug_type_likelihood,
                         cell_type, posterior_probability_sensitive, cell_type_likelihood), 
                by=c('drug','cell','experiment')) %>%
          group_by(drug, experiment) %>%
          fill(drug_type, posterior_probability_targeted, drug_type_likelihood, .direction='down') %>%
          fill(drug_type, posterior_probability_targeted, drug_type_likelihood, .direction='up') %>%
          replace_na(list(cell_type='resistant', posterior_probability_sensitive=0,cell_type_likelihood=1)) %>%
          ungroup()
  })
  saveRDS(object=intersection.fitted.list,file=file.path(opt$log_dir,'intersection.fitted.list.RDS'))
```

Posterior drug type density plot.
```{r}
p <- posterior_drug_types %>% 
  crossing(x = seq(.001, .999, .001)) %>%
  group_by(experiment) %>%
  mutate(posterior = number/sum(number)) %>%
  ungroup() %>%
    mutate(density = posterior * dbeta(x, alpha, beta)) %>%
    ggplot(aes(x, density, color = drug_type, group = drug_type)) +
    geom_line() +
    facet_wrap(~ experiment,ncol=1) + 
    theme_bw() + 
        theme(strip.text.x = element_text(size = 18),
          legend.position='bottom',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=18),
          legend.title=element_text(size=18),
          title=element_text(size=18)) +
    labs(colour="Drug Type",y='Density',x='AOC') + 
    scale_x_continuous(limits = c(0,1), breaks=c(0,.5,1)) + 
    ggtitle('Posterior Drug-Type Densities')
  ggsave(p, file=file.path(opt$log_dir,meas,paste('posterior_drug_types.pdf',sep='')),width = 12, height = 8, units = "in")
  saveRDS(p, file.path(opt$log_dir,meas,paste('posterior_drug_types.RDS',sep='')))
```



