---
title: "Untitled"
author: "Matt Ploenzke"
date: "5/8/2020"
output: html_document
---

Packages.
```{r}
library(tidyverse)
library(cowplot)
library(viridis)
theme_set(theme_bw())
```

Load intersection posterior.
```{r}
intersection.fitted.list <- readRDS('~/Desktop/Concordance/results/CTRP_GDSC_NCI60_fit/intersection.fitted.list.RDS')
```

Load posterior information for all cells/drugs/experiments.
```{r}
posterior.formatted <- readRDS('~/Desktop/Concordance/results/CTRP_GDSC_NCI60_fit/posterior.formatted.RDS')
```

Calculate correlations.
```{r}
twoway_agreement <- tibble()
for (comp in names(intersection.fitted.list)) {
  tibb <- intersection.fitted.list[[comp]]
  curr_studies <- strsplit(comp,'_')[[1]]
  pearson <- tibb %>% 
    filter(drug_type=='broad') %>%
    select(drug, cell, realized_value, experiment) %>%
    spread(experiment, realized_value) %>% 
    na.omit() %>%
    rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
    group_by(drug) %>%
    summarise(pearson_aac = cor(v1,v2,method='pearson'),
              pearson_aac_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$se,
              pearson_aac_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$p,
              spearman_aac = cor(v1,v2,method='spearman'),
              spearman_aac_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$se,
              spearman_aac_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$p) %>%
    ungroup()
  pearson_posterior <- tibb %>% 
    filter(drug_type=='broad') %>%
    select(drug, cell, posterior_probability_sensitive, experiment) %>%
    spread(experiment, posterior_probability_sensitive) %>% 
    na.omit() %>%
    rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
    group_by(drug) %>%
    summarise(pearson_posterior = cor(v1,v2,method='pearson'),
              pearson_posterior_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$se,
              pearson_posterior_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$p,
              spearman_posterior = cor(v1,v2,method='spearman'),
              spearman_posterior_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$se,
              spearman_posterior_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$p) %>%
    ungroup()
  drug_types <- tibb %>%
    select(drug, drug_type, experiment, posterior_probability_targeted) %>%
    distinct() %>%
    filter((posterior_probability_targeted>.5 & drug_type=='targeted') | (posterior_probability_targeted<.5 & drug_type=='broad')) %>%
    select(-drug_type) %>%
    spread(experiment, posterior_probability_targeted) %>%
    rename(study1_drugtype = curr_studies[1], study2_drugtype = curr_studies[2]) %>%
    mutate(type = case_when(study1_drugtype*study2_drugtype > (1-study1_drugtype)*(1-study2_drugtype) ~ 'targeted',
                            TRUE ~ 'broad')) %>%
    select(drug, type)
  mcc_counts_rounded <- tibb %>% 
    filter(drug_type=='targeted') %>%
    select(drug, cell, cell_type, experiment) %>%
    spread(experiment, cell_type) %>% 
    na.omit() %>%
    rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
    group_by(drug) %>%
    summarise(t00 = sum(v1=='resistant' & v2=='resistant'),
              t11 = sum(v1=='sensitive' & v2=='sensitive'),
              t01 = sum(v1=='resistant' & v2=='sensitive'),
              t10 = sum(v1=='sensitive' & v2=='resistant')) %>%
       mutate(t00 = pmax(t00,.5),
              t11 = pmax(t11,.5),
              t10 = pmax(t10,.5),
              t01 = pmax(t01,.5)) %>% 
         ungroup() %>%
         mutate(#lor_rounded = log((t00*t11)/(t01*t10)),
                #lor_rounded_se = sqrt(((1/t00)+(1/t11)+(1/t01) + (1/t10))),
                pearson_roundedcounts = (t00*t11-t01*t10)/sqrt((t11+t01)*(t11+t10)*(t00+t10)*(t00+t01))) %>%
    select(drug, pearson_roundedcounts)
  mcc_rounded <- tibb %>% 
    filter(drug_type=='targeted') %>%
    select(drug, cell, cell_type, experiment) %>%
    spread(experiment, cell_type) %>% 
    na.omit() %>%
    rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
    mutate(v1 = as.numeric(v1=='sensitive'),
           v2 = as.numeric(v2=='sensitive')) %>%
    group_by(drug) %>%
    summarise(pearson_celltype = cor(v1,v2,method='pearson'),
              pearson_celltype_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$se,
              pearson_celltype_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$p,
              spearman_celltype = cor(v1,v2,method='spearman'),
              spearman_celltype_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$se,
              spearman_celltype_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$p) %>%
    ungroup() %>%
    select(drug, pearson_celltype, pearson_celltype_se, pearson_celltype_q, spearman_celltype, spearman_celltype_se, spearman_celltype_q)
  mcc_soft <- tibb %>% 
    filter(drug_type=='targeted') %>%
    select(drug, cell, posterior_probability_sensitive, experiment) %>%
    spread(experiment, posterior_probability_sensitive) %>% 
    na.omit() %>%
    rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
    group_by(drug) %>%
    summarise(pearson_soft = cor(v1,v2,method='pearson'),
              pearson_soft_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$se,
              pearson_soft_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$p,
              spearman_soft = cor(v1,v2,method='spearman'),
              spearman_soft_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$se,
              spearman_soft_q = psych::corr.test(x=v1,y=v2,use='pairwise',method='spearman',adjust='fdr')$p) %>%
    ungroup() %>%
    select(drug, pearson_soft, pearson_soft_se, pearson_soft_q, spearman_soft, spearman_soft_se, spearman_soft_q)
  mcc_counts_soft <- tibb %>% 
    filter(drug_type=='targeted') %>%
    select(drug, cell, posterior_probability_sensitive, experiment) %>%
    spread(experiment, posterior_probability_sensitive) %>% 
    na.omit() %>%
    rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
    group_by(drug) %>%
    summarise(t00 = sum((1-v1)*(1-v2)),
              t11 = sum(v1*v2),
              t01 = sum((1-v1)*v2),
              t10 = sum(v1*(1-v2))) %>%
   mutate(t00 = pmax(t00,.5),
          t11 = pmax(t11,.5),
          t10 = pmax(t10,.5),
          t01 = pmax(t01,.5)) %>% 
    ungroup() %>%
    mutate(#lor_soft = log((t00*t11)/(t01*t10)),
           #lor_soft_se = sqrt(((1/t00)+(1/t11)+(1/t01) + (1/t10))),
           pearson_softcounts = (t00*t11-t01*t10)/sqrt((t11+t01)*(t11+t10)*(t00+t10)*(t00+t01))) %>%
    select(drug, pearson_softcounts)
  twoway_agreement <- pearson %>% 
    left_join(pearson_posterior, by='drug') %>% 
    left_join(mcc_counts_rounded, by='drug') %>% 
    left_join(mcc_counts_soft, by='drug') %>%
    left_join(mcc_rounded, by='drug') %>%
    left_join(mcc_soft, by='drug') %>%
    left_join(drug_types, by='drug') %>%
    mutate(comparison = comp) %>% 
    bind_rows(twoway_agreement)
}
```

Exploratory plot comparing correlation measures.
```{r}
library(ggrepel)
twoway_agreement %>%
  mutate(color = case_when(type == 'targeted' ~ 'D',
                           TRUE ~ 'A')) %>%
  ggplot(aes(x=pearson_aac, y=pearson_posterior)) +
  geom_abline(aes(slope=1,intercept=0),lty=2) +
  geom_text_repel(aes(label=drug)) +
  geom_point(aes(fill=color),alpha=.5, size=4, shape=21,color='black') + 
  theme(panel.grid = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.position='none') +
  scale_fill_viridis(discrete = TRUE,direction = -1) +
  scale_x_continuous(breaks=c(-.5,0,.5,1), limits = c(-.5,1)) + 
  scale_y_continuous(breaks=c(-.5,0,.5,1), limits = c(-.5,1)) + 
  facet_wrap(vars(comparison),ncol=3)
ggsave('temp.png',width=14,height=5,units='in')
```

Same things but with standard errors.
```{r}
twoway_agreement %>%
  pivot_longer(-c('drug','type', 'comparison'), names_to='measure', values_to = 'value') %>% 
  separate(measure, into=c('correlation','method','metric'),fill = 'right', remove=TRUE) %>%
  replace_na(list(metric='estimate')) %>%
  pivot_wider(names_from='metric',values_from='value') %>%
  mutate(color = case_when(type == 'targeted' ~ 'red',
                           TRUE ~ 'black')) %>%
  mutate(drug=reorder(as.factor(drug),estimate)) %>%
  filter(!(method %in% c('roundedcounts','softcounts'))) %>%
  #filter(correlation !=  'spearman') %>%
  filter(type == 'targeted', method %in% c('aac','soft', 'celltype')) %>%
  ggplot(aes(x=drug, y=estimate, group=method, fill=method)) +
  geom_hline(aes(yintercept=0),lty=2) +
  geom_errorbar(aes(ymin=estimate-1.96*se, ymax=estimate+1.96*se),position=position_dodge(width=1)) +
  geom_point(alpha=.5, size=4, shape=21,color='black',position=position_dodge(width=1)) + 
  theme(panel.grid = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.position='top') +
  scale_fill_viridis(discrete = TRUE,direction = -1) +
  coord_flip() +
  facet_grid(cols=vars(comparison),rows=vars(correlation))
ggsave('temp.png',width=14,height=5,units='in')
```

Bootstrap.
```{r}
twoway_agreement_bootstrapped <- tibble()
global_agreement <- tibble()
for (ii in 1:1000) {
  for (comp in names(intersection.fitted.list)) {
    tibb <- intersection.fitted.list[[comp]]
    curr_studies <- strsplit(comp,'_')[[1]]
    pearson <- tibb %>%
      filter(drug_type=='broad') %>%
      select(drug, cell, realized_value, experiment) %>%
      spread(experiment, realized_value) %>% 
      na.omit() %>%
      sample_n(size=n(),replace = TRUE) %>%
      rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
      group_by(drug) %>%
      summarise(pearson_aac = cor(v1,v2,method='pearson'),
                pearson_aac_se = psych::corr.test(x=v1,y=v2,use='pairwise',method='pearson',adjust='fdr')$se,
                pearson_aac_shuf = cor(sample(v1,n(),replace = FALSE),v2, method='pearson'),
                spearman_aac = cor(v1,v2,method='spearman')) %>%
      ungroup()
    pearson_posterior <- tibb %>% 
      filter(drug_type=='broad') %>%
      select(drug, cell, posterior_probability_sensitive, experiment) %>%
      spread(experiment, posterior_probability_sensitive) %>% 
      na.omit() %>%
      sample_n(size=n(),replace = TRUE) %>%
      rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
      group_by(drug) %>%
      summarise(pearson_posterior = cor(v1,v2,method='pearson'),
                pearson_posterior_shuf = cor(sample(v1,n(),replace = FALSE),v2, method='pearson'),
                spearman_posterior = cor(v1,v2,method='spearman')) %>%
      ungroup()
    drug_types <- tibb %>%
      select(drug, drug_type, experiment, posterior_probability_targeted) %>%
      distinct() %>%
      #filter((posterior_probability_targeted>.5 & drug_type=='targeted') | (posterior_probability_targeted<.5 & drug_type=='broad')) %>%
      filter(drug_type == 'targeted') %>%
      select(-drug_type) %>%
      group_by(drug) %>%
      mutate(type = rbinom(1,1,sample(unique(posterior_probability_targeted),1))) %>%
      mutate(type = case_when(type==1 ~ 'targeted', TRUE ~ 'broad')) %>%
      ungroup() %>%
      spread(experiment, posterior_probability_targeted) %>%
      rename(study1_drugtype = curr_studies[1], study2_drugtype = curr_studies[2]) %>%
      #mutate(type = case_when(study1_drugtype*study2_drugtype > (1-study1_drugtype)*(1-study2_drugtype) ~ 'targeted',
      #                        TRUE ~ 'broad')) %>%
      select(drug, type)
     mcc_rounded <- tibb %>% 
      filter(drug_type=='targeted') %>%
      select(drug, cell, posterior_probability_sensitive, experiment) %>%
      spread(experiment, posterior_probability_sensitive) %>% 
      na.omit() %>%
       sample_n(size=n(),replace = TRUE) %>%
      rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
      mutate(v1 = rbinom(n(),1,v1),v2 = rbinom(n(),1,v2)) %>%
      group_by(drug) %>%
      mutate(t00 = sum(v1==0 & v2==0),
              t11 = sum(v1==1 & v2==1),
              t01 = sum(v1==0 & v2==1),
              t10 = sum(v1==1 & v2==0)) %>%
      group_by(drug, t11, t10, t01, t00) %>%
      summarise(pearson_celltype = cor(v1,v2,method='pearson'),
                pearson_celltype_shuf = cor(sample(v1,n(),replace = FALSE),v2, method='pearson'),
                spearman_celltype = cor(v1,v2,method='spearman')) %>%
      ungroup() %>%
      mutate(pearson_celltype = case_when(is.na(pearson_celltype) & t01==0 & t10==0 ~ 1,
                                                  is.na(pearson_celltype) & (t01!=0 | t10!=0) ~ 0,
                                                  TRUE ~ pearson_celltype),
             spearman_celltype = case_when(is.na(spearman_celltype) & t01==0 & t10==0 ~ 1,
                                                  is.na(spearman_celltype) & (t01!=0 | t10!=0) ~ 0,
                                                  TRUE ~ spearman_celltype)) %>%
      select(drug, pearson_celltype, pearson_celltype_shuf, spearman_celltype)
    mcc_soft <- tibb %>% 
      filter(drug_type=='targeted') %>%
      select(drug, cell, posterior_probability_sensitive, experiment) %>%
      spread(experiment, posterior_probability_sensitive) %>% 
      na.omit() %>%
      sample_n(size=n(),replace = TRUE) %>%
      rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
      group_by(drug) %>%
      summarise(pearson_soft = cor(v1,v2,method='pearson'),
                spearman_soft = cor(v1,v2,method='spearman')) %>%
      ungroup() %>%
      select(drug, pearson_soft, spearman_soft)
    twoway_agreement_bootstrapped <- pearson %>% 
      left_join(pearson_posterior, by='drug') %>% 
      left_join(mcc_rounded, by='drug') %>%
      left_join(mcc_soft, by='drug') %>%
      left_join(drug_types, by='drug') %>%
      mutate(comparison = comp, rep=ii) %>% 
      bind_rows(twoway_agreement_bootstrapped)
  }
  tdat <- tibble()
  for (comp in names(intersection.fitted.list)) {
    tibb <- intersection.fitted.list[[comp]]
    curr_studies <- strsplit(comp,'_')[[1]]
    tdat <- tibb %>% 
      group_by(drug) %>%
      mutate(drug_type_sim = rbinom(1,1,sample(unique(posterior_probability_targeted),1))) %>%
      ungroup()  %>%
      filter((drug_type=='targeted' & drug_type_sim==1) | (drug_type=='broad' & drug_type_sim==0)) %>%
      select(drug, cell, posterior_probability_sensitive, experiment,  drug_type) %>%
      mutate(posterior_probability_sensitive =  case_when(drug_type=='targeted' ~ as.numeric(rbinom(n(),1,posterior_probability_sensitive)),
                                                          TRUE ~ posterior_probability_sensitive)) %>%
      select(-drug_type) %>%
      spread(experiment, posterior_probability_sensitive) %>% 
      na.omit() %>%
      rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
      mutate(v1 = rbinom(n(),1,v1),v2 = rbinom(n(),1,v2)) %>%
      mutate(comparison = comp) %>%
      bind_rows(tdat)
  }
  global_agreement <- tdat %>% 
    mutate(v1 = as.numeric(v1),
           v2 = as.numeric(v2)) %>%
    mutate(unique_row_id = 1:n()) %>% #The rows need to be unique for `spread` to work.
    mutate(dummy = 1) %>% 
    spread(comparison, dummy, fill = 0) %>% 
    group_by(drug) %>%
    mutate(t00 = sum(v1==0 & v2==0),
              t11 = sum(v1==1 & v2==1),
              t01 = sum(v1==0 & v2==1),
              t10 = sum(v1==1 & v2==0)) %>% 
    group_by(drug, t11, t10, t01, t00) %>%
    mutate(v3 = sample(v1,n(),replace=FALSE),
           CTRP_GDSC2 = sample(CTRP_GDSC,n(),replace=FALSE),
           CTRP_NCI602 = sample(CTRP_NCI60,n(),replace=FALSE),
           GDSC_NCI602 = sample(GDSC_NCI60,n(),replace=FALSE)) %>%
    do(global_corr = ppcor::pcor.test(.$v1,.$v2,.[,c('CTRP_GDSC','CTRP_NCI60','GDSC_NCI60')])$estimate,
       global_corr_shuf = ppcor::pcor.test(.$v3,.$v2,.[,c('CTRP_GDSC2','CTRP_NCI602','GDSC_NCI602')])$estimate) %>%
    ungroup() %>%
   mutate(global_corr = unlist(global_corr),
           global_corr_shuf = unlist(global_corr_shuf),
           rep=ii) %>% 
    mutate(global_corr = case_when(is.na(global_corr) & t01==0 & t10==0 ~ 1,
                                                  is.na(global_corr) & (t01!=0 | t10!=0) ~ 0,
                                                  TRUE ~ global_corr),
             global_corr_shuf = case_when(is.na(global_corr_shuf) & t01==0 & t10==0 ~ 1,
                                                  is.na(global_corr_shuf) & (t01!=0 | t10!=0) ~ 0,
                                                  TRUE ~ global_corr_shuf)) %>%
    select(-t00,-t11,-t01,-t10) %>%
    bind_rows(global_agreement)
}
```

Bootstrap drug types.
```{r}
drugs_agreement_bootstrapped <- tibble()
for (ii in 1:1000) {
  for (comp in names(intersection.fitted.list)) {
    tibb <- intersection.fitted.list[[comp]]
    curr_studies <- strsplit(comp,'_')[[1]]
     drugs_agreement_bootstrapped <- tibb %>% 
      distinct(drug, posterior_probability_targeted, experiment, drug_type) %>%
      filter(drug_type == 'targeted') %>%
      spread(experiment, posterior_probability_targeted) %>% 
      na.omit() %>%
      rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
      mutate(v1 = rbinom(n(),1,v1),v2 = rbinom(n(),1,v2)) %>%
      summarise(pearson_drugtype = cor(v1,v2,method='pearson'),
                pearson_drugtype_shuf =  cor(sample(v1,n(),replace = FALSE),v2, method='pearson'),
                spearman_drugtype = cor(v1,v2,method='spearman')) %>%
      select(pearson_drugtype, pearson_drugtype_shuf, spearman_drugtype) %>%
       mutate(rep = ii, comparison = comp) %>%
       bind_rows(drugs_agreement_bootstrapped)
  }
}
library(ggpubr)
library(ggsci)
my_colors <- list("CTRP and GDSC"="#767676FF", 'CTRP and NCI60'="#800000FF", "GDSC and NCI60"="#FFA319FF")
my_comparisons <- list( c("CTRP and NCI60", "CTRP and GDSC"),c("GDSC and NCI60", "CTRP and GDSC"),c("CTRP and NCI60", "GDSC and NCI60"))
ggerrorplot(drugs_agreement_bootstrapped %>% 
  mutate(comparison = gsub('_',' and ',comparison)) %>% 
  mutate(comparison = factor(comparison, levels=names(my_colors))), 
  x = "comparison", y = "pearson_drugtype", color='black',fill=NA,
  alpha=.5,
  ylab = '', xlab='Comparison', add = "mean_sd",
  title = 'Correlation between sampled drug type',
  legend='none')+ 
  geom_violin(aes(fill=comparison),color='black',alpha=.3,adjust=2.5) + 
  scale_fill_manual(values=my_colors) +
  stat_compare_means(comparisons = my_comparisons,label = 'p.signif')
ggsave('temp.png',width=8,height = 5,units='in')


drugs_agreement_bootstrapped %>% 
  mutate(comparison = gsub('_',' and ',comparison)) %>%
  ggplot(aes(x=comparison,y=pearson_drugtype)) + 
  geom_jitter(aes(fill=comparison),color='black',shape=21,alpha=.75,size=2,width=.15,height=0) +
  geom_violin(aes(fill=comparison),trim=TRUE,adjust=2,alpha=.5) + 
  #geom_violin(inherit.aes=FALSE,aes(x=comparison, y=pearson_drugtype_shuf),trim=FALSE,fill='grey',adjust=2,alpha=.5) + 
  geom_hline(aes(yintercept=1)) + 
  geom_hline(aes(yintercept=0)) + 
  geom_hline(aes(yintercept=.5),lty=2) + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  #lims(y=c(0,1)) +
  theme(panel.grid = element_blank()) + 
  labs(x='Pairwise comparison',y='Correlation')
```

GGpubr drug-level comparison.
```{r}
tdat <- twoway_agreement_bootstrapped %>%
  pivot_longer(-c('drug','type', 'comparison','rep'), names_to='measure', values_to = 'value') %>% 
  separate(measure, into=c('correlation','method','metric'),fill = 'right', remove=TRUE) %>%
  replace_na(list(metric='estimate')) %>%
  pivot_wider(names_from='metric',values_from='value') %>%
  mutate(color = case_when(type == 'targeted' ~ 'red',
                           TRUE ~ 'black')) %>%
  filter(correlation !=  'spearman') %>%
  #filter(type == 'targeted', method %in% c('aac', 'celltype')) %>%
  filter((type=='broad' & method %in% c('posterior')) | (type=='targeted' & method %in% c('celltype'))) %>%
  mutate(method = case_when(method=='aac' ~ 'raw', TRUE ~ 'posterior')) %>% 
  mutate(drug=reorder(as.factor(drug),estimate)) %>%
  select(drug, estimate, comparison, rep) %>% 
  filter(!is.na(estimate)) %>%
  group_by(drug, rep) %>% 
  filter(n_distinct(comparison)==3) %>%
  ungroup() %>% 
  mutate(comparison = gsub('_',' and ',comparison))
library(ggpubr)
get_palette('uchicago')
my_colors <- list("CTRP and GDSC"="#767676FF", 'CTRP and NCI60'="#800000FF", "GDSC and NCI60"="#FFA319FF")
my_comparisons <- list( c("CTRP and NCI60", "CTRP and GDSC"),c("GDSC and NCI60", "CTRP and GDSC"),c("CTRP and NCI60", "GDSC and NCI60"))
ggviolin(tdat %>% group_by(comparison, drug) %>% summarise(estimate = mean(estimate)) %>% ungroup() %>% 
           mutate(comparison =  factor(comparison, levels=names(my_colors))), 
  x = "comparison", y = "estimate", color='black',fill='comparison',
  alpha=.3,
  ylab = '', xlab='Comparison', add = "jitter", adjust = 2, draw_quantiles = c(.25,0.5,.75),
  title = 'Correlation between sampled cell type',
  legend='none')+ 
  scale_fill_manual(values = my_colors) +
  stat_compare_means(comparisons = my_comparisons,paired = TRUE)
ggsave('temp.png',width=8,height = 5,units='in')
```

Bootstrapped correlations plot.
```{r}
twoway_agreement_bootstrapped %>%
  pivot_longer(-c('drug','type', 'comparison','rep'), names_to='measure', values_to = 'value') %>% 
  separate(measure, into=c('correlation','method','metric'),fill = 'right', remove=TRUE) %>%
  replace_na(list(metric='estimate')) %>%
  pivot_wider(names_from='metric',values_from='value') %>%
  mutate(color = case_when(type == 'targeted' ~ 'red',
                           TRUE ~ 'black')) %>%
  mutate(drug=reorder(as.factor(drug),estimate)) %>%
  filter(correlation !=  'spearman') %>%
  filter(type == 'targeted', method %in% c('aac','soft', 'celltype')) %>%
  ggplot(aes(x=drug, y=estimate, fill=method)) +
  geom_hline(aes(yintercept=0),lty=2) +
  geom_boxplot() + 
  theme(panel.grid = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.position='top') +
  scale_fill_viridis(discrete = TRUE,direction = -1) +
  coord_flip() +
  facet_grid(cols=vars(comparison),rows=vars(correlation))
ggsave('temp.png',width=14,height=5,units='in')
```

Naive two-way agreement.
```{r}
library(ggrepel)
twoway_agreement %>%
  mutate(color = case_when(type == 'targeted' ~ 'D',
                           TRUE ~ 'A')) %>%
  ggplot(aes(x=spearman, y=pearson)) +
  geom_abline(aes(slope=1,intercept=0),lty=2) +
  geom_text_repel(aes(label=drug)) +
  geom_point(aes(fill=color),alpha=.5, size=4, shape=21,color='black') + 
  theme(panel.grid = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.position='none') +
  scale_fill_viridis(discrete = TRUE,direction = -1) +
  scale_x_continuous(breaks=c(-.5,0,.5,1), limits = c(-.5,1)) + 
  scale_y_continuous(breaks=c(-.5,0,.5,1), limits = c(-.5,1)) + 
  labs(x='Spearman rank correlation', y='Pearson correlation') +
  facet_wrap(vars(comparison),ncol=3)
ggsave('temp.png',width=14,height=5,units='in')
```

Bar plot like shown in cellminer paper.
```{r}
tdat <- twoway_agreement %>% 
  select(drug, pearson_aac_q, comparison) %>%
  group_by(comparison) %>%
  arrange(desc(pearson_aac_q)) %>%
  mutate(reproducibility_rank_score = row_number()-1) %>% 
  ungroup() %>%
  mutate(reproducibility_rank_score = reproducibility_rank_score/max(reproducibility_rank_score)) %>% 
  group_by(drug) %>%
  summarise(reproducibility_rank_score = mean(reproducibility_rank_score)) %>% 
  ungroup() 
p1 <- tdat %>% 
  ggplot(aes(x=reorder(drug,reproducibility_rank_score), y=reproducibility_rank_score,fill=drug)) + 
  geom_bar(stat='identity',color='black', alpha=.6) + 
  theme_bw() + 
  theme(plot.title=element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position='none') +
  scale_fill_viridis_d()
tdat2 <- global_agreement %>% 
  replace_na(list(global_corr = 0)) %>%
  group_by(drug) %>%
  summarise(agreement = mean(global_corr)) %>%
  ungroup()
p2 <- tdat2 %>% 
  ggplot(aes(y=reorder(drug,agreement), x=agreement, fill=drug)) + 
  geom_bar(stat='identity',color='black', alpha=.6) + 
  theme_bw() + 
  theme(plot.title=element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position='none') +
  scale_fill_viridis_d()
library(ggrepel) 
p3 <- tdat2 %>%
  arrange(agreement) %>%
  mutate(agreement = row_number()-1) %>%
  mutate(agreement = agreement/max(agreement)) %>%
  left_join(tdat, by='drug') %>%
  ggplot(aes(x=reproducibility_rank_score, y=agreement)) + 
  stat_smooth(method='lm',se=FALSE,formula = y~x) + 
  geom_abline(aes(slope=1,intercept=0),lty=2) + 
  geom_text_repel(aes(label=drug),min.segment.length = 0, box.padding = 0.5) + 
  geom_point(fill='grey', size=4,shape=21,color='black',alpha=.6) + 
  theme_bw() +
  scale_x_continuous(breaks=c(0,.5,1), limits = c(0,1)) + 
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0,1)) + 
  theme(plot.title=element_blank(),
        legend.position='none',
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  scale_fill_viridis_d() + 
  labs(x='Reproducibility rank score',y='Estimated posterior rank score')
ggsave('temp.png',width=8,height=8,units='in')

ggdraw() +
  draw_plot(p3,0,0,.85,.85) +
  draw_plot(p1,.05,.85,.80,.15) +
  draw_plot(p2,.85,.05,.15,.80) 
```

Relationship between rank and correlation.
```{r}
tdat <- twoway_agreement %>% 
  select(drug, pearson_aac_q, comparison) %>%
  group_by(comparison) %>%
  arrange(desc(pearson_aac_q)) %>%
  mutate(reproducibility_rank_score = row_number()-1) %>% 
  ungroup() %>%
  mutate(reproducibility_rank_score = reproducibility_rank_score/max(reproducibility_rank_score)) %>% 
  group_by(drug) %>%
  summarise(reproducibility_rank_score = mean(reproducibility_rank_score)) %>% 
  ungroup() 

tdat2 <- twoway_agreement %>% 
  select(drug, pearson_aac, comparison) %>%
  group_by(drug) %>%
  summarise(agreement = mean(pearson_aac)) %>% 
  ungroup() 

tdat2 %>%
  left_join(tdat, by='drug') %>%
  ggplot(aes(x=reproducibility_rank_score, y=agreement)) + 
  geom_label_repel(aes(label=drug)) + 
  geom_point(size=4,shape=21,color='black',alpha=.8) + 
  geom_abline(aes(slope=1,intercept=0),lty=2) + 
  stat_smooth(method='lm') + 
  theme_bw() +
  lims(x=c(-.1,1),y=c(-.1,1))

```

Similar but with correlation instead of rank.
```{r}
tdat <- twoway_agreement %>% 
  select(drug, pearson_aac, comparison) %>%
  group_by(drug) %>%
  summarise(reproducibility_rank_score = mean(pearson_aac)) %>% 
  ungroup() 
p1 <- tdat %>% 
  ggplot(aes(x=reorder(drug,reproducibility_rank_score), y=reproducibility_rank_score)) + 
  geom_bar(stat='identity') + 
  theme_bw() + 
  theme(plot.title=element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
tdat2 <- global_agreement %>% 
  replace_na(list(global_corr = 0)) %>%
  group_by(drug) %>%
  summarise(agreement = mean(global_corr)) %>%
  ungroup()
p2 <- tdat2 %>% 
  ggplot(aes(y=reorder(drug,agreement), x=agreement)) + 
  geom_bar(stat='identity') + 
  theme_bw() + 
  theme(plot.title=element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) 

p3 <- tdat2 %>%
  left_join(tdat, by='drug') %>%
  ggplot(aes(x=reproducibility_rank_score, y=agreement)) + 
  geom_label_repel(aes(label=drug)) + 
  geom_point(size=4,shape=21,color='black',alpha=.8) + 
  geom_abline(aes(slope=1,intercept=0),lty=2) + 
  stat_smooth(method='lm') + 
  theme_bw() +
  lims(x=c(-.1,1),y=c(-.1,1))

ggdraw() +
  draw_plot(p3,0,0,.85,.85) +
  draw_plot(p1,.05,.85,.80,.15) +
  draw_plot(p2,.85,.05,.15,.80) 
```

Plot two-way agreement for all drugs of pearson correlation for each comparison.
```{r}
twoway_agreement %>% 
  select(drug, pearson, comparison) %>%
  spread(comparison, pearson) %>%
  ggplot(aes(x=CTRP_NCI60, y=GDSC_NCI60)) + 
  geom_abline(aes(slope=1,intercept=0), lty=1, color='grey') +
  geom_hline(aes(yintercept=0),lty=2, color='grey') +
  geom_vline(aes(xintercept=0),lty=2, color='grey') +
  geom_point(alpha=.75) + 
  theme_bw() + 
  scale_color_viridis(discrete=TRUE) + 
  lims(y=c(-1,1),x=c(-1,1)) + 
  theme(panel.grid = element_blank())
ggsave('temp.png',width=4,height=4,units='in')
```

Boxplot of these comparisons.
```{r}
library(ggpubr)
my_comparisons <- list( c("CTRP_GDSC", "CTRP_NCI60"),c("GDSC_NCI60", "CTRP_GDSC"),c("CTRP_NCI60", "GDSC_NCI60"))
ggboxplot(twoway_agreement, 
  x = "comparison", y = "pearson", color='comparison',palette = "jco",
  ylab = '', xlab='Dataset', 
  title='Pearson correlation',
  subtitle='Restricted to cells/drugs present in all three studiess',
  legend='none',
  width=.5)+ 
  stat_compare_means(comparisons = my_comparisons)
ggsave('temp.png',width=6,height=6,units='in')
```

Plot two-way agreements for all drugs.
```{r}
library(ggrepel)
twoway_agreement %>%
  mutate(posterior = case_when(type=='targeted' ~ MCC,
                               TRUE ~ pearson_posterior)) %>%
  mutate(Correlation = case_when(type=='targeted' ~ 'Matthews',
                               TRUE ~ 'Spearman')) %>%
  mutate(comparison = gsub('_', ' and ',comparison)) %>% 
ggplot(aes(x=spearman, y=posterior)) + 
  geom_abline(aes(slope=1,intercept=0),lty=2) +
  geom_text_repel(aes(label=drug)) +
  geom_point(aes(fill=Correlation),alpha=.5, size=4, shape=21,color='black') + 
  theme(panel.grid = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.position='none') +
  scale_fill_viridis(discrete = TRUE) +
  scale_x_continuous(breaks=c(0,.5,1), limits = c(-.3,1)) + 
  scale_y_continuous(breaks=c(0,.5,1), limits = c(-.3,1)) + 
  labs(x='Pearson correlation (raw AAC)', y='Correlation (model-based)') + 
  facet_wrap(vars(comparison),ncol=3)
ggsave('temp.png',width=8,height=8,units='in')
```

Boxplot of agreements.
```{r}
library(ggpubr)
my_comparisons <- list( c("CTRP and GDSC", "CTRP and NCI60"),c("GDSC and NCI60", "CTRP and GDSC"),c("CTRP and NCI60", "GDSC and NCI60"))
ggboxplot(twoway_agreement %>%
  mutate(posterior = case_when(type=='targeted' ~ soft_MCC,
                               TRUE ~ spearman_posterior)) %>%
  mutate(Correlation = case_when(type=='targeted' ~ 'Matthews',
                               TRUE ~ 'Spearman')) %>%
  select(drug, spearman, posterior, comparison) %>%
  gather('Method','Correlation', spearman, posterior) %>%
  mutate(Method = case_when(Method=='spearman' ~ 'Spearman rank (raw AAC)',
                            TRUE ~ 'Correlation (model-based)'),
         comparison = gsub('_',' and ',comparison)), 
  x = "comparison", y = "Correlation", color='comparison',palette = "jco",
  ylab = 'Correlation', xlab='Pairwise comparison', facet.by = c('Method'),
  legend='top',
  width=.5)+ 
  stat_compare_means(comparisons = my_comparisons) + 
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
  labs(color='')
ggsave('temp.png',width=8,height=6,units='in')
```

Two-way plots comparing raw values between study.
```{r}
dir.create('twoway_plots', showWarnings=FALSE)
for (comp in names(intersection.fitted.list)) {
  tibb <- intersection.fitted.list[[comp]]
  curr_studies <- strsplit(comp,'_')[[1]]
  drugss <- tibb %>% distinct(drug) %>% pull()
  for (dr in drugss) {
    p1 <- tibb %>%
      filter(drug == dr) %>% 
      filter(drug_type == 'broad') %>%
      select(drug, cell, experiment, realized_value) %>%
      spread(experiment, realized_value) %>%
      rename(v1 = curr_studies[1], v2 = curr_studies[2]) %>%
      ggplot(aes(x=v1, y=v2)) + 
      geom_point() + 
      geom_smooth(method='lm',se=FALSE) + 
      theme_bw() +
      #lims(x=c(0,1),y=c(0,1)) + 
      labs(x=curr_studies[1],y=curr_studies[2])
      ggsave(plot=p1, filename=paste('twoway_plots/',dr,'_',comp,'.png',sep=''),width=12,height=12,units='in')
  }
}
```

Drug type plot.
```{r}
drug_types_agreement <- tibble()
for (comp in names(intersection.fitted.list)) {
  curr_studies <- strsplit(comp,'_')[[1]]
  drug_types_agreement <- intersection.fitted.list[[comp]] %>% 
    mutate(posterior_probability_targeted = round(posterior_probability_targeted,digits=2)) %>%
    distinct(drug, experiment, posterior_probability_targeted) %>% 
    spread(experiment, posterior_probability_targeted) %>%
    rename(study1_targeted = curr_studies[1], study2_targeted = curr_studies[2]) %>%
    mutate(comparison = comp) %>% 
    bind_rows(drug_types_agreement)
}
drug_types_agreement %>%
  ggplot(aes(x=study1_targeted, y=study2_targeted)) + 
  geom_point(alpha=.5, size=2) + 
  theme_bw() + 
  facet_grid(cols=vars(comparison))
```

Bar plot of MCC of drug-type agreement.
```{r}
drug_types_agreement %>% 
  mutate(study1_targeted = case_when(study1_targeted >=.5 ~ 'targeted', TRUE ~ 'broad'),
         study2_targeted = case_when(study2_targeted >=.5 ~ 'targeted', TRUE ~ 'broad')) %>%
  group_by(comparison) %>%
    summarise(t00 = sum(study1_targeted=='broad' & study2_targeted=='broad'),
              t11 = sum(study1_targeted=='targeted' & study2_targeted=='targeted'),
              t01 = sum(study1_targeted=='broad' & study2_targeted=='targeted'),
              t10 = sum(study1_targeted=='targeted' & study2_targeted=='broad')) %>%
  ungroup() %>%
  mutate(prop_agree = (t00+t11)/(t00+t11+t10+t01)) %>% 
  group_by(comparison) %>%
       mutate(t00 = pmax(t00,.5),
              t11 = pmax(t11,.5),
              t10 = pmax(t10,.5),
              t01 = pmax(t01,.5)) %>% 
         ungroup() %>%
         mutate(LOR = log((t00*t11)/(t01*t10)),
                SE_LOR = sqrt(((1/t00)+(1/t11)+(1/t01) + (1/t10))),
                MCC = (t00*t11-t01*t10)/sqrt((t11+t01)*(t11+t10)*(t00+t10)*(t00+t01))) %>%
    select(comparison, LOR, SE_LOR, MCC, prop_agree) %>%
  mutate(comparison = gsub('_',' and ',comparison)) %>%
  ggplot(aes(x=reorder(comparison, -prop_agree), y=prop_agree)) + 
  geom_col() + 
  theme(panel.grid = element_blank(),
        axis.text.y = element_text(size=14),
        axis.text.x = element_text(angle=45,hjust=1),
        axis.title = element_text(size=14),
        legend.position='none') +
  #scale_fill_brewer(palette='Dark2') +
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0,1)) + 
  labs(x='', y='Proportion') 
ggsave('temp.png', width=5,height=4,units='in')
```

Drug type plot.
```{r}
drug_types_agreement <- tibble()
for (comp in names(intersection.fitted.list)) {
  curr_studies <- strsplit(comp,'_')[[1]]
  drug_types_agreement <- intersection.fitted.list[[comp]] %>% 
    mutate(posterior_probability_targeted = round(posterior_probability_targeted,digits=2)) %>%
    distinct(drug, experiment, posterior_probability_targeted) %>% 
    spread(experiment, posterior_probability_targeted) %>%
    rename(study1_targeted = curr_studies[1], study2_targeted = curr_studies[2]) %>%
    mutate(comparison = comp) %>% 
    bind_rows(drug_types_agreement)
}

drug_types_agreement %>%
  mutate(color = case_when(study1_targeted*study2_targeted < (1-study1_targeted)*(1-study2_targeted) ~ 'A',
                           TRUE ~ 'D')) %>%
  pivot_longer(study1_targeted:study2_targeted, names_to = 'study',values_to='value') %>%
  separate(comparison, into=c('study1','study2'),sep='_',remove = FALSE) %>%
  mutate(study = case_when(study=='study1_targeted' ~ study1, 
                           study=='study2_targeted' ~ study2)) %>%
  select(-study1,-study2) %>%
  mutate(value = value - .5) %>% 
  ggplot(aes(x=reorder(drug,-value), y=value, fill=study)) + 
  geom_bar(aes(color=color), stat='identity',position='dodge', alpha=.9, color='black') +  
  geom_hline(aes(yintercept=0),lty=1) + 
  theme(panel.grid = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position='bottom') +
  scale_y_continuous(breaks=c(-.5,-.25,0,.25,.5), labels= c(0,.25,.5,.75,1)) + 
  scale_x_discrete(expand = c(0,2)) + 
  annotate('text',x=0,y=.325, label='More targeted',size=5) +
  annotate('text',x=39.5,y=-.325, label='Less targeted',size=5) +
  geom_segment(aes(x=-.75, y = .25, xend=-.75, yend = .4), colour='black', size=.25,
               arrow = arrow(angle=20, length = unit(.25, "cm"),type='closed')) +
  geom_segment(aes(x=38.75, y = -.25, xend=38.75, yend = -.4), colour='black', size=.25,
               arrow = arrow(angle=20, length = unit(.25, "cm"),type='closed')) +
  labs(x='', y='Estimated drug targetedness',fill='') + 
  coord_flip() + 
  scale_fill_brewer(palette = "Set1")
ggsave('temp.png',width=6,height=10,units='in')
```