---
title: "Estimate posteriors across PRISM"
author: "Matt Ploenzke"
output: html_document
---

Packages

```{r}
library(tidyverse)
library(PharmacoMixtuR)
```

Set options

```{r}
datasets = c('PRISM','GDSC','CTRP') # CCLE GDSC GDSC1000 gCSI FIMM CTRPv2
exclude_zeros = FALSE
prism_dir = file.path('~/Downloads', 'prism')
output_dir = file.path('~/Downloads', 'results', paste(paste(datasets,collapse='_'),
                                                       paste0('zeros_', iflese(exclude_zeros,'excluded','included')),
                                                       sep='_'))
dir.create(output_dir, showWarnings = FALSE, recursive=TRUE)
```

Name fixes

```{r}
name_fixes <- list("gw-843682x" = "BRD-K90382497", "jq1-(+)" = "BRD-K54606188", "sb-525334" = "BRD-K37720887", 
                   "nutlin-3" = "BRD-A12230535", "fk-866" = "BRD-K58550667", 'cisplatin' = "BRD-K69172251", 
                   "tipifarnib" = "BRD-K62965247","jq1-(+)" = "BRD-K54606188","idelalisib" = "BRD-K60866521",
                   "i-bet-762" = "BRD-K08109215","zstk-474" = "BRD-K63068307","5-fluorouracil" = "BRD-K24844714",
                   "mitomycin-c" = "BRD-A48237631","fk-866" = "BRD-K58550667","tozasertib" = "BRD-K59369769",
                   'cisplatin' = "BRD-K69172251","gw-843682x" = "BRD-K90382497","tipifarnib" = "BRD-K62965247",
                   "jq1-(+)" = "BRD-K54606188","idelalisib" = "BRD-K60866521","i-bet-762" = "BRD-K08109215",
                   "sb-525334" = "BRD-K37720887","zstk-474" = "BRD-K63068307","nutlin-3" = "BRD-A12230535",
                   "5-fluorouracil" = "BRD-K24844714","mitomycin-c" = "BRD-A48237631","fk-866" = "BRD-K58550667",
                   "tozasertib" = "BRD-K59369769")
```

Load prism
 - Files downloaded from DepMap
    - https://depmap.org/portal/download/all/?release=PRISM+Repurposing+19Q4&file=secondary-screen-dose-response-curve-parameters.csv
    - https://depmap.org/portal/download/all/?release=Sanger+GDSC1+and+GDSC2&file=sanger-dose-response.csv
    - https://depmap.org/portal/download/all/?release=CTRP+CTD%5E2&file=CTRPv2.0_2015_ctd2_ExpandedDataset.zip
  
```{r}
prism <- read.csv(file.path(prism_dir,"secondary-screen-dose-response-curve-parameters.csv"), stringsAsFactors=FALSE) %>% 
  as_tibble() %>%
  select(broad_id, depmap_id, ccle_name, screen_id, name, moa, target, disease.area, auc, row_name, passed_str_profiling) %>% 
  mutate(name = tolower(name))
for (nname in 1:length(name_fixes)) {
  prism <- prism %>%
    mutate(name = case_when(broad_id == name_fixes[nname] ~ names(name_fixes)[nname],
                            TRUE ~ name))
}
```

Cell line name concordance

```{r}
cell_concordance <- prism %>%
  distinct(ccle_name, row_name)
```

Format PRISM

```{r}
prism <- prism %>%
  filter(screen_id == 'HTS002') %>%
  rename(drug = name, 
         cell = row_name, 
         value = auc) %>%
  mutate(experiment = 'PRISM',
         measure = auc) %>%
  select(drug, cell, value, experiment, measure) %>%
  distinct(drug, cell, experiment, measure, .keep_all = TRUE) %>%
  na.omit() %>%
  filter(drug!='',cell!='') %>% 
  mutate(value = 1-pmin(value,1))
```

Load GDSC

```{r}
gdsc <- read.csv(file.path(prism_dir, 'sanger-dose-response.csv'), stringsAsFactors = FALSE) %>% 
  as_tibble() %>%
  select(DATASET, COSMIC_ID, DRUG_ID, ARXSPAN_ID, DRUG_NAME, BROAD_ID, AUC_PUBLISHED, auc) %>%
  rename_all(tolower) %>%
  mutate(drug_name = tolower(drug_name)) %>%
  rename(name = drug_name)
for (nname in 1:length(name_fixes)) {
  gdsc <- gdsc %>%
    mutate(name = case_when(broad_id == name_fixes[nname] ~ names(name_fixes)[nname],
                            TRUE ~ name))
}
gdsc <- gdsc %>%
  rename(drug = name, 
         cell = arxspan_id, 
         value = auc) %>%
  mutate(experiment = 'GDSC',
         measure = auc) %>%
  arrange(desc(dataset)) %>%
  select(drug, cell, value, experiment, measure) %>%
  distinct(drug, cell, experiment, measure, .keep_all = TRUE) %>%
  na.omit() %>%
  filter(drug!='') %>%
  mutate(value = 1-value)
```

Load CTRP

```{r}
ctrp <- read.delim(file.path(prism_dir,'CTRPv2.0_2015_ctd2_ExpandedDataset/v20.data.curves_post_qc.txt'),stringsAsFactors = FALSE) %>%
  as_tibble() %>%
  select(experiment_id, area_under_curve, master_cpd_id, conc_pts_fit) %>%
  mutate(area_under_curve = area_under_curve/conc_pts_fit) %>%
  select(-conc_pts_fit)
cpds <- read.delim(file.path(prism_dir,'CTRPv2.0_2015_ctd2_ExpandedDataset/v20.meta.per_compound.txt'),stringsAsFactors = FALSE) %>%
  as_tibble()
experis <-  read.delim(file.path(prism_dir,'CTRPv2.0_2015_ctd2_ExpandedDataset/v20.meta.per_experiment.txt'),stringsAsFactors = FALSE) %>%
  as_tibble()
cellls <- read.delim(file.path(prism_dir,'CTRPv2.0_2015_ctd2_ExpandedDataset/v20.meta.per_cell_line.txt'),stringsAsFactors = FALSE) %>%
  as_tibble()
ctrp <- ctrp %>%
  left_join(cpds %>% select(master_cpd_id, cpd_name, broad_cpd_id), by=c('master_cpd_id')) %>%
  left_join(experis %>% select(experiment_id, master_ccl_id), by=c('experiment_id')) %>%
  left_join(cellls %>% select(master_ccl_id, ccl_name, ccle_primary_site), by=c('master_ccl_id'))  %>%
  unite(ccle_name, ccl_name, ccle_primary_site,sep='_',remove = TRUE) %>%
  mutate(ccle_name = tolower(ccle_name)) %>%
  mutate(cpd_name = tolower(cpd_name)) %>%
  rename(name = cpd_name)
for (nname in 1:length(name_fixes)) {
  ctrp <- ctrp %>%
    mutate(name = case_when(broad_cpd_id == name_fixes[nname] ~ names(name_fixes)[nname],
                            TRUE ~ name))
}
rm(cpds, experis, cellls)
ctrp <- ctrp %>% 
  rename(drug = name, 
         cell = ccle_name, 
         value = area_under_curve) %>%
  mutate(experiment = 'CTRP',
         measure = auc) %>%
  select(drug, cell, value, experiment, measure) %>%
  distinct(drug, cell, experiment, measure, .keep_all = TRUE) %>%
  na.omit() %>% 
  filter(drug!='') %>%
  mutate(value = 1-pmin(value,1)) %>%
  rename(ccle_name = cell) %>%
  mutate(ccle_name = tolower(ccle_name)) %>%
  left_join(cell_concordance %>% mutate(ccle_name = tolower(ccle_name)), by='ccle_name')  %>%
  na.omit() %>% 
  rename(cell = row_name) %>%
  select(-ccle_name) %>%
  select(drug, cell, value, experiment, measure)
```

Cat these together into a list for individual fits

```{r}
sensitivity.tibble.list <- list(PRISM=prism, CTRP=ctrp, GDSC=gdsc)
if (exclude_zeros) {
  sensitivity.tibble.list <- lapply(sensitivity.tibble.list, function(tt) {
    tt %>% filter(value > 0)
  })
}
```

Cat these into a list for the intersection cells and drugs

```{r}
full.intersection <- ctrp %>% 
  bind_rows(prism, gdsc) %>% 
  group_by(cell, drug) %>% 
  filter(n_distinct(experiment)==3) %>%
  ungroup()
intersection.tibble.list <- list('CTRP_PRISM' = full.intersection %>% filter(experiment %in% c('CTRP', 'PRISM')),
                                 'GDSC_PRISM' = full.intersection %>% filter(experiment %in% c('GDSC', 'PRISM')),
                                 'CTRP_GDSC' = full.intersection %>% filter(experiment %in% c('CTRP', 'GDSC')))
```

Remove PSets

```{r}
rm(prism, ctrp, name_fixes, gdsc, nname)
```

Initialize drug and cell assignments

```{r}
drugs.tibble.list <- lapply(sensitivity.tibble.list, function(li) {
  drug_dat <- li %>% 
    mutate(all_median = quantile(value,.6),
           all_mad = stats::mad(value),
           drug=as.factor(drug)) %>% 
    group_by(drug) %>% 
    mutate(median=median(value),
           mad=stats::mad(value),
           all_median=first(all_median),
           all_mad=first(all_mad)) %>%
    ungroup() %>%
    mutate(drug_type = ifelse(median<=all_median & mad<=all_mad,'targeted','broad')) %>%
    distinct(drug, drug_type, all_median, all_mad, median, median, mad)
  li %>% 
    left_join(drug_dat, by='drug') %>%
    mutate(sensitive = ifelse(value > all_median, 1,0)) %>%
    group_by(drug, measure, drug_type) %>%
    summarise(p_prior = mean(sensitive),
              sensitive = sum(sensitive),
              cell_count = n()) %>%
    ungroup() %>% 
    select(drug, measure, p_prior, sensitive, cell_count, drug_type)
})
cells.tibble.list <- lapply(1:length(sensitivity.tibble.list), function(li) {
  sensitivity.tibble.list[[li]] %>% 
    left_join(drugs.tibble.list[[li]], by=c('drug','measure')) %>% 
    select(drug:measure,drug_type) %>%
    ungroup() %>% 
    group_by(experiment) %>%
    mutate(prior_threshold = quantile(value,probs = .6), 
           cell_type = ifelse(value>=prior_threshold,'sensitive','resistant')) %>%
    ungroup()
})
names(cells.tibble.list) <- names(drugs.tibble.list)
```

Fit distributions and use these to initialize EM

```{r}
meas <- auc
drug_types_list <- lapply(drugs.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    group_by(drug_type) %>%
    do(mutate(fit_bb_mle(.$sensitive, .$cell_count), number = nrow(.))) %>%
    ungroup() %>%
    mutate(drug_type_prior = number / sum(number))
})
targetted_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  ttibb <- tibb %>%
    filter(measure==meas) %>%
    mutate(value = ifelse(value==0,1e-3,value)) %>%
    mutate(drug_type = 'targeted') %>%
    group_by(drug, cell_type, drug_type, experiment) %>%
    do(mutate(fit_beta_mle(.$value),number = nrow(.))) %>%
    group_by(drug, drug_type, experiment) %>%
    mutate(ndist=n_distinct(cell_type)) %>%
    ungroup()
  ttibb %>%
    bind_rows(
      ttibb %>% 
        filter(ndist<2) %>% 
        mutate(cell_type2 = case_when(cell_type=='resistant' ~ 'sensitive',cell_type=='sensitive' ~ 'resistant'),
               cell_type=cell_type2,
               number=0,
               alpha=case_when(cell_type == 'resistant' ~ .5,
                               cell_type == 'sensitive' ~ 50),
               beta=case_when(cell_type == 'resistant' ~ 7.5,
                              cell_type == 'sensitive' ~ 50)) %>%
        select(-cell_type2)
    ) %>%
    group_by(drug, experiment) %>%       
    mutate(targeted_cell_type_prior = number / sum(number)) %>%
    ungroup() %>% 
    select(-ndist)
})
broad_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    mutate(x=ifelse(value==0,1e-3,value)) %>%
    group_by(drug, experiment) %>%
    do(mutate(fit_beta_mle(.$x),
              number = nrow(.),
              broad_cell_type_prior = mean(.$value>=.$prior_threshold))) %>%
    ungroup() %>% 
    mutate(drug_type = 'broad') %>%
    select(drug, drug_type, alpha, beta, number, broad_cell_type_prior, experiment)
})
targeted_drug_priors <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_fits_list[[num]] %>% 
    rename(cell_type_prior = targeted_cell_type_prior) %>%
    select(drug, drug_type, cell_type_prior, experiment, cell_type) %>%
    mutate(drug_type = 'broad')
})
broad_drug_priors <- lapply(1:length(broad_drug_fits_list), function(num) {
  broad_drug_fits_list[[num]] %>%
    rename(cell_type_prior = broad_cell_type_prior) %>%
    select(drug, drug_type, cell_type_prior, experiment) %>%
    mutate(drug_type = 'targeted')
})
```

Perform an expectation step

```{r}
targetted_cell_assignments_list <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_list <- unique(targetted_drug_fits_list[[num]]$drug)
  targetted_cell_assignments <- lapply(targetted_drug_list, function(dr) {
    cells.tibble.list[[num]] %>%
      filter(drug == dr,measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'targeted') %>%
      mutate(value=ifelse(value<1e-3,1e-3,value)) %>%
      crossing(targetted_drug_fits_list[[num]] %>% filter(drug == dr) %>% select(-drug,-drug_type) %>% rename(experiment1=experiment)) %>%
      filter(experiment==experiment1) %>% 
      select(-experiment1) %>% 
      mutate(median = qbeta(.5,alpha,beta),
             likelihood = dbeta(value, alpha, beta)) %>% 
      group_by(cell_type) %>%
      mutate(max.likelihood=max(likelihood)) %>%
      ungroup() %>%
      mutate(likelihood = case_when(value>median & cell_type == 'sensitive' ~ max.likelihood-likelihood + max.likelihood, 
                                    value<median & cell_type == 'resistant' ~ max.likelihood-likelihood + max.likelihood, 
                                    TRUE~likelihood)) %>%
      mutate(likelihood = targeted_cell_type_prior * likelihood) %>%
      group_by(drug, cell, experiment) %>%
      mutate(posterior=exp(log(likelihood)-log(sum(likelihood)))) %>% 
      top_n(1, likelihood) %>%
      ungroup()
  })
  do.call(bind_rows, targetted_cell_assignments)
})
broad_cell_assignments_list <- lapply(1:length(broad_drug_fits_list), function(num) {
  cells.tibble.list[[num]] %>%
      filter(drug %in% unique(broad_drug_fits_list[[num]]$drug),measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'broad') %>%
      mutate(value=ifelse(value<1e-3,1e-3,value)) %>%
      left_join(broad_drug_fits_list[[num]], by=c('drug','drug_type', 'experiment')) %>%
      mutate(likelihood = dbeta(value, alpha, beta),
             cell_type = ifelse((broad_cell_type_prior*pbeta(value, alpha, beta)) >
                                  ((1-broad_cell_type_prior)*(1-pbeta(value, alpha, beta))),
                                'sensitive','resistant'))
})

drugs.tibble.list <- lapply(1:length(drugs.tibble.list), function(num) {
  targetteds <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(targetted_cell_assignments_list[[num]] %>% select(drug, cell, cell_type, likelihood), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>% 
    mutate(type='targeted')
  broads <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(broad_cell_assignments_list[[num]] %>% select(drug, cell, cell_type), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>%
    mutate(type='broad')
  bind_rows(targetteds, broads)
})

drug_assignments_list <- lapply(1:length(drugs.tibble.list), function(num) {
  drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    rename(drug_type = type) %>%
    right_join(drug_types_list[[num]] %>% select(-number), by='drug_type') %>%
    mutate(likelihood = drug_type_prior * VGAM::dbetabinom.ab(sensitive, cell_count, alpha, beta)) %>%
    group_by(drug) %>%
    mutate(posterior=likelihood/sum(likelihood)) %>% 
    top_n(1, likelihood) %>%
    ungroup()
})

cell_assignments_list <- lapply(1:length(targetted_cell_assignments_list), function(num) {
  bind_rows(targetted_cell_assignments_list[[num]],broad_cell_assignments_list[[num]]) %>%
    left_join(targeted_drug_priors[[num]], by=c('drug','experiment','drug_type','cell_type')) %>%
    mutate(targeted_cell_type_prior = case_when(is.na(targeted_cell_type_prior) & drug_type=='broad' ~ cell_type_prior,
                                                TRUE ~ targeted_cell_type_prior)) %>%
    select(-cell_type_prior) %>%
    left_join(broad_drug_priors[[num]],  by=c('drug','experiment','drug_type')) %>%
    mutate(broad_cell_type_prior = case_when(is.na(broad_cell_type_prior) & drug_type=='targeted' ~ cell_type_prior,
                                                TRUE ~ broad_cell_type_prior)) %>%
    select(-cell_type_prior) %>%
    right_join(drug_assignments_list[[num]] %>% select(drug, drug_type), by=c('drug','drug_type')) %>% 
    select(drug, cell, value, experiment, measure, drug_type, cell_type, broad_cell_type_prior, targeted_cell_type_prior)
})
names(cell_assignments_list) <- names(drug_types_list)
```

Run EM

```{r}
iterations_list <- list()
for(num in 1:length(cell_assignments_list)) {
  drug_assignments <- drug_assignments_list[[num]]
  cell_assignments <- cell_assignments_list[[num]]
  targeted_priors <- targeted_drug_priors[[num]]
  broad_priors <- broad_drug_priors[[num]]
  iterations_list[[num]] <- accumulate(1:25, iterate_em, .init = list(drug_assignments = drug_assignments,
                                                                     cell_assignments = cell_assignments,
                                                                     targeted_priors = targeted_priors,
                                                                     broad_priors = broad_priors))
}
names(iterations_list) <- names(sensitivity.tibble.list)
```

Obtain posterior information from last rep

```{r}
posterior_drug_types_list <- lapply(names(iterations_list), function(num) {
  iterations_list[[num]] %>% 
    map_df("drug_types", .id = "iteration") %>% 
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
posterior_drug_assignments_list <- lapply(names(iterations_list), function(num) {
  iterations_list[[num]] %>% 
    map_df("drug_assignments", .id = "iteration") %>% 
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
posterior_drug_fits_list <- lapply(names(iterations_list), function(num) {
  iterations_list[[num]] %>% 
    map_df("drug_fits", .id = "iteration") %>% 
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
posterior_cell_assignments_list <- lapply(names(iterations_list), function(num) {
  iterations_list[[num]] %>% 
    map_df("cell_assignments", .id = "iteration") %>% 
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
names(posterior_cell_assignments_list) <- names(iterations_list)
```

Do one more rep

```{r}
posteriors_list <- list()
for(num in 1:length(cell_assignments_list)) {
  drug_assignments <- posterior_drug_assignments_list[[num]] %>% select(-iteration)
  cell_assignments <- posterior_cell_assignments_list[[num]]  %>% select(-iteration)
  targeted_priors <- targeted_drug_priors[[num]]
  broad_priors <- broad_drug_priors[[num]]
  posteriors_list[[num]] <- accumulate(1, iterate_em, .init = list(drug_assignments = drug_assignments,
                                                               cell_assignments = cell_assignments,
                                                                targeted_priors = targeted_priors,
                                                                     broad_priors = broad_priors),
                                       last=TRUE)
}
names(posteriors_list) <- names(sensitivity.tibble.list)

posterior_drug_types_full <- lapply(names(posteriors_list), function(num) {
  posteriors_list[[num]] %>% 
    map_df("drug_types", .id = "iteration") %>% 
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
posterior_drug_assignments_full <- lapply(names(posteriors_list), function(num) {
  posteriors_list[[num]] %>% 
    map_df("drug_assignments", .id = "iteration") %>%
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
posterior_drug_fits_full <- lapply(names(posteriors_list), function(num) {
  posteriors_list[[num]] %>% 
    map_df("drug_fits", .id = "iteration") %>% 
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
posterior_cell_assignments_full <- lapply(names(posteriors_list), function(num) {
  posteriors_list[[num]] %>% 
    map_df("cell_assignments", .id = "iteration") %>% 
    mutate(iteration = as.numeric(iteration)) %>%
    filter(iteration==max(iteration))
})
names(posterior_cell_assignments_full) <- names(posteriors_list)
```

Format posterior agreements

```{r}
posterior_drug_types <- do.call(bind_rows,posterior_drug_types_list) %>%
  mutate(experiment=rep(names(iterations_list),each=2)) 
nums <- sapply(posterior_drug_assignments_list, nrow)
posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_list) %>%
    mutate(experiment=rep(names(iterations_list),times=nums))
nums <- sapply(posterior_drug_fits_list, nrow)
posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_list) %>%
    mutate(experiment=rep(names(iterations_list),times=nums))
nums <- sapply(posterior_cell_assignments_list, nrow)
posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_list) %>%
    mutate(experiment=rep(names(iterations_list),times=nums))

posterior_drug_types <- do.call(bind_rows,posterior_drug_types_full) %>%
  mutate(experiment=rep(names(posteriors_list),each=2)) 
nums <- sapply(posterior_drug_assignments_full, nrow)
posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_full) %>%
    mutate(experiment=rep(names(posteriors_list),times=nums))
nums <- sapply(posterior_drug_fits_full, nrow)
posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_full) %>%
    mutate(experiment=rep(names(posteriors_list),times=nums))
nums <- sapply(posterior_cell_assignments_full, nrow)
posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_full) %>%
    mutate(experiment=rep(names(posteriors_list),times=nums))
```

Save posteriors

```{r}
saveRDS(object=posterior_drug_types,file=file.path(output_dir,'posterior_drug_types.RDS'))
saveRDS(object=posterior_drug_fits,file=file.path(output_dir,'posterior_drug_fits.RDS'))
saveRDS(object=posterior_drug_assignments,file=file.path(output_dir,'posterior_drug_assignments.RDS'))
saveRDS(object=posterior_cell_assignments,file=file.path(output_dir,'posterior_cell_assignments.RDS'))
```

Format data frame with posterior information

```{r}
posterior_cell_assignments <- readRDS(file=file.path(output_dir,'posterior_cell_assignments.RDS'))
posterior_drug_assignments <- readRDS(file=file.path(output_dir,'posterior_drug_assignments.RDS'))
posterior_drug_fits <- readRDS(file=file.path(output_dir,'posterior_drug_fits.RDS'))
posterior <- posterior_cell_assignments %>%
  select(drug, cell, experiment, drug_type, cell_type, posterior, likelihood, value) %>%
  rename(cell_type_posterior=posterior,
         cell_type_likelihood=likelihood,
         realized_value=value) %>%
  group_by(drug, cell) %>% 
  mutate(num_experiments = n_distinct(experiment)) %>%
  ungroup() %>%
  left_join(posterior_drug_assignments %>%
              select(drug, drug_type, posterior,likelihood, experiment) %>%
              rename(drug_type_posterior=posterior,
                     drug_type_likelihood=likelihood), by=c('drug_type','drug','experiment')) %>%
  mutate(cell_type = ifelse(cell_type == 'sensitive' & drug_type == 'broad',
                            'resistant',cell_type)) %>%
  left_join(posterior_drug_fits %>%
              select(drug, cell_type, experiment, alpha, beta, drug_type),
            by = c('drug','cell_type','experiment','drug_type')) %>%
  mutate(cell_type_posterior = case_when(drug_type == 'broad' ~ pbeta(realized_value, alpha, beta, lower.tail = FALSE),
                                         TRUE ~ cell_type_posterior)) %>%
  select(-alpha, -beta) %>%
  mutate(cell_type_posterior = ifelse((cell_type == 'resistant' & drug_type == 'targeted') | drug_type=='broad',
                                      1-cell_type_posterior,cell_type_posterior)) %>%
  mutate(drug_type_posterior = ifelse(drug_type == 'broad', 1-drug_type_posterior,drug_type_posterior)) %>%
  rename(posterior_probability_sensitive = cell_type_posterior,
         posterior_probability_targeted = drug_type_posterior)
saveRDS(object=posterior,file=file.path(output_dir,'posterior.formatted.RDS'))
```

Extract intersection data

```{r}
intersection.fitted.list <- lapply(intersection.tibble.list, function(tibb) {
  drugs_cells <- tibb %>% 
    distinct(drug,cell, experiment, measure, value) %>%
    rename(realized_value = value)
  experiments <- tibb %>% 
    distinct(experiment) %>%
    pull
  drugs_cells %>% 
    left_join(posterior %>% 
                filter(experiment %in% experiments) %>%
                select(drug, cell, experiment,
                       drug_type, posterior_probability_targeted, drug_type_likelihood,
                       cell_type, posterior_probability_sensitive, cell_type_likelihood), 
              by=c('drug','cell','experiment')) %>%
        group_by(drug, experiment) %>%
        fill(drug_type, posterior_probability_targeted, drug_type_likelihood, .direction='down') %>%
        fill(drug_type, posterior_probability_targeted, drug_type_likelihood, .direction='up') %>%
        replace_na(list(cell_type='resistant', posterior_probability_sensitive=0,cell_type_likelihood=1)) %>%
        ungroup()
})
saveRDS(object=intersection.fitted.list,file=file.path(output_dir,'intersection.fitted.list.RDS'))
```
