---
title: "Make figures"
author: "Matt Ploenzke"
output: html_document
---

The purpose of this markdown is to generate the figures in the manuscript

Libraries

```{r}
library(tidyverse)
library(viridis)
library(cowplot)
library(ggrepel)
theme_set(theme_bw())
```

File paths 

```{r}
results_dir <- '~/Downloads/results'
output_dir <- '~/Downloads/figs'
```

# Two-way posteriors comparison

Load posterior information for just CCLE and GDSC studies

```{r}
intersection.tibble.list <- readRDS(file.path(results_dir, 'CCLE_GDSC_fit_within_study/intersection.fitted.list.RDS'))
posterior_drug_types <- readRDS(file.path(results_dir,'CCLE_GDSC_fit_within_study/posterior_drug_types.RDS'))
posterior_drug_fits <- readRDS(file.path(results_dir,'CCLE_GDSC_fit_within_study/posterior_drug_fits.RDS'))
posterior_drug_assignments <- readRDS(file.path(results_dir,'CCLE_GDSC_fit_within_study/posterior_drug_assignments.RDS')) %>% filter(iteration == max(iteration))
posterior_cell_assignments <- readRDS(file.path(results_dir,'CCLE_GDSC_fit_within_study/posterior_cell_assignments.RDS')) %>% filter(iteration == max(iteration))
```

## Crizotinib

CCLE posteriors

```{r}
experi <- 'CCLE'
dr <- 'Crizotinib'
dr_type <- 'targeted'
drug_posteriors_proportions <- posterior_cell_assignments %>%
  filter(drug_type == dr_type) %>% 
  group_by(drug, experiment) %>%
  summarise(posterior = sum(cell_type=='sensitive')/n()) %>%
  ungroup()
betadens <- posterior_drug_fits %>%
  filter (experiment == experi, drug_type == dr_type) %>%
    mutate(cross = paste(cell_type, drug, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = seq(.001, .999, length = 1000),
      beta_curve = dbeta(seq(.001, .999, length = 1000), 
                           df$alpha, 
                           df$beta) 
    )
  }) %>%
  as_tibble() %>% 
  separate(cross,into=c('cell_type','drug'),sep='_') %>%
  full_join(posterior_drug_fits %>% 
              filter(experiment == experi, drug_type == dr_type) %>% 
              mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), 
            by=c('drug','cell_type')) %>% 
  left_join(drug_posteriors_proportions, by=c('drug','experiment')) %>%
  mutate(posterior = ifelse(drug_type=='broad',1,posterior)) %>%
  mutate(posterior = ifelse(drug_type=='targeted' & cell_type=='resistant',1,posterior)) %>%
  group_by(drug,cell_type) %>% 
  mutate(beta_curve = beta_curve/max(beta_curve)*posterior) %>%
  ungroup() %>%
  filter(iteration==max(iteration)) %>%
  mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
dr_type <- posterior_cell_assignments %>%
      filter(drug==dr, experiment == experi, drug_type == dr_type) %>% 
      distinct(drug_type) %>% 
      pull
p_top <- posterior_cell_assignments %>%
  filter(drug==dr, experiment == experi, drug_type == dr_type) %>%
  ggplot(aes(value,y=..scaled..)) +
    geom_density(fill=1) +
    theme_bw() + 
    theme(legend.position = 'none',
          plot.title  = element_text(size=16),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.border = element_blank(), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    scale_color_manual(values = c('resistant'='blue', 'sensitive'='orange')) + 
    labs(y='Scaled Density',x='AOC', title=paste(dr, 'sensitivities and estimated posteriors')) +
    geom_line(data=betadens %>% filter(drug==dr), aes(y = beta_curve, color=cell_type, lty=cell_type), lwd = .9) + 
    scale_y_continuous(limits = c(0,1)) + 
  scale_x_continuous(limits= c(0,.5))
cell_ty <- p_top$layers[[2]]$data %>% distinct(cell_type) %>% pull()
p_top$layers[[2]]$data <- p_top$layers[[2]]$data %>% 
  mutate(beta_curve = ifelse(cell_type == 'sensitive',beta_curve*2, beta_curve),
         beta_curve = case_when(beta_curve<.0025 & value<.25 ~ NA_real_, 
                                beta_curve<.0011 & value>.75 ~ NA_real_,
                                TRUE ~ beta_curve))
```

GDSC posteriors

```{r}
experi <- 'GDSC'
dr <- 'Crizotinib'
dr_type <- 'targeted'
drug_posteriors_proportions <- posterior_cell_assignments %>%
  filter(drug_type == dr_type) %>% 
  group_by(drug, experiment) %>%
  summarise(posterior = sum(cell_type=='sensitive')/n()) %>%
  ungroup()
betadens <- posterior_drug_fits %>%
  filter (experiment == experi, drug_type == dr_type) %>%
    mutate(cross = paste(cell_type, drug, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = seq(.001, .999, length = 1000),
      beta_curve = dbeta(seq(.001, .999, length = 1000), 
                           df$alpha, 
                           df$beta) 
    )
  }) %>%
  as_tibble() %>% 
  separate(cross,into=c('cell_type','drug'),sep='_') %>%
  full_join(posterior_drug_fits %>% 
              filter(experiment == experi, drug_type == dr_type) %>% 
              mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), 
            by=c('drug','cell_type')) %>% 
  left_join(drug_posteriors_proportions, by=c('drug','experiment')) %>%
  mutate(posterior = ifelse(drug_type=='broad',1,posterior)) %>%
  mutate(posterior = ifelse(drug_type=='targeted' & cell_type=='resistant',1,posterior)) %>%
  group_by(drug,cell_type) %>% 
  mutate(beta_curve = beta_curve/max(beta_curve)*posterior) %>%
  ungroup() %>%
  filter(iteration==max(iteration)) %>%
  mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
dr_type <- posterior_cell_assignments %>%
      filter(drug==dr, experiment == experi, drug_type == dr_type) %>% 
      distinct(drug_type) %>% 
      pull
p_side <- posterior_cell_assignments %>%
  filter(drug==dr, experiment == experi, drug_type == dr_type) %>%
  ggplot(aes(value,y=..scaled..)) +
    geom_density(fill=1) +
    theme_bw() + 
    theme(legend.position = 'none',
          plot.title  = element_text(size=16),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.border = element_blank(), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    scale_color_manual(values = c('resistant'='blue', 'sensitive'='orange')) + 
    labs(y='Scaled Density',x='AOC', title='') +
    geom_line(data=betadens %>% filter(drug==dr), aes(y = beta_curve, color=cell_type, lty=cell_type), lwd = .9) + 
    scale_y_continuous(limits = c(0,1)) + 
  scale_x_continuous(limits= c(0,.5))
cell_ty <- p_side$layers[[2]]$data %>% distinct(cell_type) %>% pull()
p_side$layers[[2]]$data <- p_side$layers[[2]]$data %>% 
  mutate(beta_curve = ifelse(cell_type == 'sensitive',beta_curve*2, beta_curve),
         beta_curve = case_when(beta_curve<.0025 & value<.25 ~ NA_real_, 
                                beta_curve<.0011 & value>.75 ~ NA_real_,
                                TRUE ~ beta_curve))
tempdat <- p_side$data 
p_side <- p_side + ggpubr::rotate()
```

Cells in common

```{r}
p_main <- intersection.tibble.list[['CCLE_GDSC']] %>%
  filter(drug==dr, drug_type == dr_type) %>% 
  select(drug,cell,experiment, measure, everything()) %>%
  gather(variable, value, -(drug:measure)) %>% 
  unite(temp, experiment, variable) %>%
  spread(temp,value) %>%
  ggplot(aes(x=as.numeric(CCLE_realized_value),y=as.numeric(GDSC_realized_value))) + 
  geom_point(alpha=.5,size=4) + 
  scale_color_brewer(palette = 'Dark2') + 
  theme_bw() + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 14),
        panel.grid = element_blank()) +
  labs(x='CCLE',y='GDSC') +
  scale_x_continuous(limits=c(0,.5),breaks = c(0,.25,.5)) + 
  scale_y_continuous(limits=c(0,.5),breaks = c(0,.25,.5)) 
fig1a <- ggdraw() +
  draw_plot(p_main,0,0,.85,.85) +
  draw_plot(p_top,.05,.85,.80,.15) +
  draw_plot(p_side,.85,.05,.15,.80) 
```

## 17-AAG

CCLE posteriors

```{r}
experi <- 'CCLE'
dr <- '17-AAG'
dr_type <- 'broad'
drug_posteriors_proportions <- posterior_cell_assignments %>%
  filter(drug_type == dr_type) %>% 
  group_by(drug, experiment) %>%
  summarise(posterior = sum(cell_type=='sensitive')/n()) %>%
  ungroup()
betadens <- posterior_drug_fits %>%
  filter (experiment == experi, drug_type == dr_type) %>%
    mutate(cross = paste(cell_type, drug, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = seq(.001, .999, length = 1000),
      beta_curve = dbeta(seq(.001, .999, length = 1000), 
                           df$alpha, 
                           df$beta) 
    )
  }) %>%
  as_tibble() %>% 
  separate(cross,into=c('cell_type','drug'),sep='_') %>%
  full_join(posterior_drug_fits %>% 
              filter(experiment == experi, drug_type == dr_type) %>% 
              mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), 
            by=c('drug','cell_type')) %>% 
  left_join(drug_posteriors_proportions, by=c('drug','experiment')) %>%
  mutate(posterior = ifelse(drug_type=='broad',1,posterior)) %>%
  mutate(posterior = ifelse(drug_type=='targeted' & cell_type=='resistant',1,posterior)) %>%
  group_by(drug,cell_type) %>% 
  mutate(beta_curve = beta_curve/max(beta_curve)*posterior) %>%
  ungroup() %>%
  filter(iteration==max(iteration)) %>%
  mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
dr_type <- posterior_cell_assignments %>%
      filter(drug==dr, experiment == experi, drug_type == dr_type) %>% 
      distinct(drug_type) %>% 
      pull
p_top <- posterior_cell_assignments %>%
  filter(drug==dr, experiment == experi, drug_type == dr_type) %>%
  ggplot(aes(value,y=..scaled..)) +
    geom_density(fill=1) +
    theme_bw() + 
    theme(legend.position = 'none',
          plot.title  = element_text(size=16),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.border = element_blank(), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    scale_color_manual(values = c('resistant'='blue', 'sensitive'='orange')) + 
    labs(y='Scaled Density',x='AOC', title = paste(dr, 'sensitivities and estimated posteriors')) +
    geom_line(data=betadens %>% filter(drug==dr), aes(y = beta_curve, color=cell_type), lwd = .9) + 
    scale_y_continuous(limits = c(0,1)) 
```

GDSC posteriors

```{r}
experi <- 'GDSC'
dr <- '17-AAG'
dr_type <- 'broad'
drug_posteriors_proportions <- posterior_cell_assignments %>%
  filter(drug_type == dr_type) %>% 
  group_by(drug, experiment) %>%
  summarise(posterior = sum(cell_type=='sensitive')/n()) %>%
  ungroup()
betadens <- posterior_drug_fits %>%
  filter (experiment == experi, drug_type == dr_type) %>%
    mutate(cross = paste(cell_type, drug, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = seq(.001, .999, length = 1000),
      beta_curve = dbeta(seq(.001, .999, length = 1000), 
                           df$alpha, 
                           df$beta) 
    )
  }) %>%
  as_tibble() %>% 
  separate(cross,into=c('cell_type','drug'),sep='_') %>%
  full_join(posterior_drug_fits %>% 
              filter(experiment == experi, drug_type == dr_type) %>% 
              mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), 
            by=c('drug','cell_type')) %>% 
  left_join(drug_posteriors_proportions, by=c('drug','experiment')) %>%
  mutate(posterior = ifelse(drug_type=='broad',1,posterior)) %>%
  mutate(posterior = ifelse(drug_type=='targeted' & cell_type=='resistant',1,posterior)) %>%
  group_by(drug,cell_type) %>% 
  mutate(beta_curve = beta_curve/max(beta_curve)*posterior) %>%
  ungroup() %>%
  filter(iteration==max(iteration)) %>%
  mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
dr_type <- posterior_cell_assignments %>%
      filter(drug==dr, experiment == experi, drug_type == dr_type) %>% 
      distinct(drug_type) %>% 
      pull
p_side <- posterior_cell_assignments %>%
  filter(drug==dr, experiment == experi, drug_type == dr_type) %>%
  ggplot(aes(value,y=..scaled..)) +
    geom_density(fill=1) +
    theme_bw() + 
    theme(legend.position = 'none',
          plot.title  = element_text(size=16),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.border = element_blank(), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    scale_color_manual(values = c('resistant'='blue', 'sensitive'='orange')) + 
    labs(y='Scaled Density',x='AOC',  title='') +
    geom_line(data=betadens %>% filter(drug==dr), aes(y = beta_curve, color=cell_type), lwd = .9) + 
    scale_y_continuous(limits = c(0,1)) +
  ggpubr::rotate()
```

Cells in common

```{r}
p_main <- intersection.tibble.list[['CCLE_GDSC']] %>%
  filter(drug==dr, drug_type == dr_type) %>% 
  select(drug,cell,experiment, measure, everything()) %>%
  gather(variable, value, -(drug:measure)) %>% 
  unite(temp, experiment, variable) %>%
  spread(temp,value) %>%
  ggplot(aes(x=as.numeric(CCLE_realized_value),y=as.numeric(GDSC_realized_value))) + 
  geom_point(alpha=.5,size=4) + 
  scale_color_brewer(palette = 'Dark2') + 
  theme_bw() + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 14),
        panel.grid = element_blank()) +
  labs(x='CCLE',y='GDSC') +
  scale_x_continuous(limits=c(0,1),breaks = c(0,.5,1)) + 
  scale_y_continuous(limits=c(0,1),breaks = c(0,.5,1)) 
fig1b <- ggdraw() +
  draw_plot(p_main,0,0,.85,.85) +
  draw_plot(p_top,.05,.85,.80,.15) +
  draw_plot(p_side,.85,.05,.15,.80) 
```

## Combine
```{r}
fig1 <- plot_grid(fig1a, fig1b, labels = c('a)', 'b)'), label_size = 16)
ggsave(file.path(output_dir, 'posteriors.pdf'), width=12,height=6, units='in')
```

# Drug type and accuracy comparison

Load intersection posterior (just CCLE and GDSC)

```{r}
intersection.fitted.list <- readRDS(file.path(results_dir,'CCLE_GDSC_fit_within_study/intersection.fitted.list.RDS'))
```

Dug type

```{r}
fig2a <- intersection.fitted.list[[1]] %>% 
  distinct(drug, experiment, drug_type, posterior_probability_targeted) %>%
  filter(drug_type == 'targeted') %>% 
  pivot_wider(names_from=experiment,values_from=posterior_probability_targeted) %>%
  ggplot(aes(x=CCLE, y=GDSC)) + 
  geom_vline(xintercept=.5, lty=2) +
  geom_hline(yintercept=.5, lty=2) + 
  geom_text_repel(aes(label=drug),force=10) +
  geom_point(shape=21,size=2.5,alpha=.75,fill='grey') +
  scale_x_continuous(breaks=c(0,.5,1)) +
  scale_y_continuous(breaks=c(0,.5,1)) +
  theme(panel.grid = element_blank(),
        axis.text  = element_text(size=14),
        axis.title  = element_text(size=14),
        plot.title  = element_text(size=16)) + 
  labs(title = 'Estimated drug targetedness') 
```

Accuracy

```{r}
fig2b <- intersection.fitted.list[[1]] %>% 
  filter(drug_type=='targeted', !(drug %in% c('17-AAG','paclitaxel','PD-0325901'))) %>% 
  select(drug,  cell, experiment, realized_value) %>% 
  pivot_wider(names_from = experiment, values_from = realized_value) %>%
  group_by(drug) %>% 
  summarise(spearman = cor(CCLE, GDSC, method='spearman')) %>%
  ungroup() %>%
  left_join(intersection.fitted.list[[1]] %>% 
    filter(drug_type=='targeted', !(drug %in% c('17-AAG','paclitaxel','PD-0325901'))) %>% 
    select(drug,  cell, experiment, cell_type) %>%
      pivot_wider(names_from = experiment, values_from = cell_type) %>%
    group_by(drug) %>% 
    summarise(accuracy = mean((CCLE=='sensitive' & GDSC=='sensitive') | (CCLE=='resistant' & GDSC=='resistant'))) %>%
    ungroup(), by='drug') %>%
  ggplot(aes(x=spearman, y=accuracy)) + 
  geom_text_repel(aes(label=drug)) +
  geom_point(shape=21,size=2.5,alpha=.75, fill='grey') +
  theme(#panel.grid = element_blank(),
        axis.text  = element_text(size=14),
        axis.title  = element_text(size=14),
        plot.title  = element_text(size=16)) + 
  scale_y_continuous(limits = c(-.1,1),labels = c(0,.5,1), breaks=c(0,.5,1)) +  
  scale_x_continuous(limits = c(-.1,1), labels = c(0,.5,1), breaks=c(0,.5,1)) +
  labs(title = 'Estimated cell agreement',
       x = "Spearman rank correlation",
       y = "Accuracy")
```

Combine 

```{r}
fig2 <- plot_grid(fig2a, fig2b, labels = c('a)', 'b)'), label_size = 16)
ggsave(file.path(output_dir, 'prop_agree.pdf'), width=12,height=6, units='in')
```

# Biomarker comparison

Load biomarkers

```{r}
all_effect_sizes <- read_csv(file.path(results_dir,'CCLE_GDSC_biomarkers_rna/all_effect_sizes.csv')) %>%
  mutate(Feature = 'RNA') %>%
  bind_rows(read_csv(file.path(results_dir,'CCLE_GDSC_biomarkers_cnv/all_effect_sizes.csv')) %>%
  mutate(Feature = 'CNV')) %>%
  bind_rows(read_csv(file.path(results_dir, 'CCLE_GDSC_biomarkers_mutation/all_effect_sizes.csv')) %>%
  mutate(Feature = 'Mutation'))
```

CAT plot

```{r}
tdat <- all_effect_sizes %>% 
  filter((Method=='Binarized' & !(Drug %in% c('17-AAG','paclitaxel','PD-0325901')))) %>% 
  filter(Dataset!='Joint') %>%
  filter(symbol != 'waterfall', Measure!='waterfall') %>%
  select(symbol, Feature, entrezgene_id, adj.P.Val, Measure, Dataset, Drug) %>%
  distinct() %>%
  group_by(Drug, Dataset, Measure) %>% 
  arrange(adj.P.Val) %>%
  mutate(Rank = row_number()) %>%
  ungroup() %>%
  select(-adj.P.Val, -entrezgene_id) %>%
  pivot_wider(names_from=Dataset,values_from=Rank) %>%
  group_by(Drug, Measure) %>%
  mutate(GDSC_count = max(GDSC,na.rm=TRUE),
         CCLE_count = max(CCLE,na.rm=TRUE)) %>%
  ungroup() %>%
  mutate_if(is.integer, as.double) %>%
  mutate(GDSC = case_when(is.na(GDSC) ~ GDSC_count+1,
                          TRUE ~ GDSC),
         CCLE = case_when(is.na(CCLE) ~ CCLE_count+1,
                          TRUE ~ CCLE)) 
pdat <- tibble()
for (dr in unique(tdat$Drug)) {
  for (meas in unique(tdat$Measure)) {
    ttdat <- tdat %>% 
      filter(Drug==dr, Measure == meas)
    max_list <- min(unique(ttdat$GDSC_count),unique(ttdat$CCLE_count))
    for (ii in seq(1,max_list/10,length.out = 1000)) {
    #for (ii in seq(1,500, by=1)) {
      pdat <- ttdat %>% 
        filter(GDSC <= ii | CCLE <= ii) %>%
        summarise(percent_in_common = sum(GDSC <= ii & CCLE <= ii)/ii*100) %>%
        mutate(List_Size = ii,
               Drug = dr, 
               Measure = meas,
               List_Length = max_list) %>%
        bind_rows(pdat)
    }
  }
}
fig3a <- pdat %>% 
  mutate(Measure = case_when(Measure=='AAC' ~ 'AAC-based',
                             TRUE ~ 'Model-based')) %>%
  ggplot(aes(x=List_Size/max_list,y=percent_in_common,color=Measure)) + 
  geom_line() + 
  theme_bw() + 
  facet_wrap(vars(Drug),ncol=4, scales='free') + 
  theme(panel.grid = element_blank(), 
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14),
        plot.title = element_text(size=16),
        legend.position='bottom') +
  scale_color_grey() + 
  labs(x= 'Relative List Size (%)',y='Genes In Common (%)', color='',
       title='Relative list size agreement') + 
  scale_y_continuous(limits = c(0,100),labels = c(0,100), breaks=c(0,100)) + 
  scale_x_continuous(limits = c(0,.075),labels = c('0','5'), breaks=c(0,.05))
```

Test statistic arrows plot

```{r}
all_effect_sizes <- read_csv(file.path(results_dir,'CCLE_GDSC1000_CTRPv2_FIMM_gCSI_biomarkers_rna/all_effect_sizes.csv')) %>% 
  filter(Drug=='Crizotinib')  %>%
  filter((Dataset=='Joint' & Measure=='Posterior' & Method=='Binarized') | 
           (Dataset=='Joint' & Measure=='AAC' & Method == 'Binarized')) %>%
  distinct()

fig3b  <- all_effect_sizes %>% 
  filter(isKnown) %>%
  select(symbol, Feature, t, Measure) %>%
  spread(Measure, t) %>% 
  replace_na(list(AAC=0, Posterior=0)) %>%
  arrange(Posterior) %>%
  mutate(yy=row_number(),
         color = (Posterior>AAC & Posterior>=0) | (Posterior<AAC & Posterior<=0)) %>%
  ggplot(aes(x=AAC, xend=Posterior,
             y=reorder(symbol,yy),yend=reorder(symbol,yy),
             color = color)) + 
  geom_vline(aes(xintercept=0),lty=1) + 
  geom_vline(aes(xintercept=-3),lty=2,alpha=.2) + 
  geom_vline(aes(xintercept=3),lty=2,alpha=.2) + 
  geom_segment(arrow=arrow(angle=20, length=unit(.25,'cm'))) + 
  theme_bw() + 
  labs(x='Test statistic', y='',
       title = 'Change in test statistic') + 
  lims(x=c(-3.5,7.5)) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(size=16),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.position = 'none') + 
  scale_color_viridis_d(option = "viridis", end=.5) 
```

Combine

```{r}
fig3 <- plot_grid(fig3a, fig3b, labels = c('a)', 'b)'), label_size = 16, rel_widths = c(2,1))
ggsave(file.path(output_dir, 'biomarkers.pdf'), width=12,height=6, units='in')
```

# PRISM proportion of zeros comparison

```{r}
intersection.fitted.list <- readRDS(file.path(results_dir,'PRISM_GDSC_CTRP_zeros_included/intersection.fitted.list.RDS'))
p_zero <- tibble()
for (comp in names(intersection.fitted.list)) {
  p_zero <- intersection.fitted.list[[comp]] %>%
    group_by(drug, experiment, drug_type) %>%
    summarise(prop_zero = mean(realized_value<=1e-2)) %>%
    ungroup() %>%
    mutate(comparison = comp) %>%
    bind_rows(p_zero)
}
p_zero %>%  
  select(drug, experiment, prop_zero) %>%
  ggplot(aes(x=experiment,y=prop_zero)) + 
  geom_boxplot(width=.5) +
  theme_bw() +
  theme(plot.title = element_text(size=16),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        legend.position = 'none') +
  labs(y='', title='Proportion of cells exhibiting no response per drug')
ggsave(file.path(output_dir, 'prop_zeros.pdf'),width=6,height=6,units='in')
```

# Pathways comparison

```{r}
pathway_path <- file.path(results_dir, 'CCLE_GDSC1000_CTRPv2_FIMM_gCSI_pathway_rna_2')
drugs <- list.dirs(pathway_path,full.names=FALSE)
drugs <- drugs[drugs!='']
KEGG_tibble <- tibble()
for (dr in drugs) {
  filles <- list.files(file.path(pathway_path,dr))
  for (fi in filles) {
    if (grepl('KEGG',fi)) { 
      KEGG_tibble <- read_csv(file.path(pathway_path,dr,fi)) %>%
        as_tibble() %>%
        mutate(File=fi, Drug=dr) %>%
        bind_rows(KEGG_tibble)
    }
  }
}
KEGG_tibble <- KEGG_tibble %>%
  mutate(File = gsub('KEGG_','',File)) %>%
  mutate(File = gsub('.csv','',File)) %>%
  separate(File,  into=c('Measure','Measure2','Dataset'),sep='_',fill='right',remove=TRUE) %>% 
  select(-Measure2) %>% 
  mutate(Dataset =  case_when((Dataset=='sensitive' | is.na(Dataset)) ~ 'Joint',
                              TRUE ~ Dataset)) %>%
  mutate(Measure = case_when(Measure == 'naive' ~ 'AAC',
                             Measure == 'posterior'  ~ 'Posterior',
                             Measure == 'cell'  ~ 'Cell type',
                             Measure == 'auc' ~ 'Numeric-AAC'))
plot_dat <- KEGG_tibble %>% 
  filter(Measure %in% c("AAC", "Cell type"), Dataset=='Joint') %>%
  unite(Measure, Measure, Dataset, sep=' ') %>%
  mutate(P=pmin(P.Up, P.Down)) %>%
  mutate(Up = case_when(P.Up < P.Down ~ 'Up',
                        TRUE ~ 'Down')) %>%
  select(Pathway, Measure, P, Drug) %>% 
  arrange(P) %>%
  distinct(Pathway, Measure, Drug, .keep_all = TRUE) %>%
  mutate(P = -log10(P)) %>%
  spread(Measure, P) %>% 
  replace_na(list(`AAC Joint`=0, `Cell type Joint`=0)) %>%
  rename(Comparison = `AAC Joint`) %>%
  rename(myMethod = `Cell type Joint`) 
pp <- plot_dat %>%
    mutate(color = case_when(str_detect(Pathway,'kinase') |  
                               str_detect(Pathway,'JAK') | 
                               str_detect(Pathway,'ALK') | 
                               str_detect(Pathway, "Pathways in cancer") |
                               str_detect(Pathway, "Antineoplastic") |
                               str_detect(Pathway, "Non-small cell lung cancer") ~ 5,
                           Comparison>= -log10(.05) & myMethod < -log10(.05) ~ 1,
                           Comparison< -log10(.05) & myMethod>= -log10(.05) ~ 2,
                           Comparison >= -log10(.05) | myMethod>= -log10(.05) ~ 3,
                           TRUE ~ 4)) %>% 
  mutate(Pathway = case_when(color == 5 ~ Pathway,
                             Comparison>= -log10(1e-3) ~Pathway,
                             myMethod >= -log10(1e-5) ~ Pathway,
                             TRUE ~ '')) %>%
  ggplot(aes(x=Comparison, y=myMethod, color=as.factor(color))) + 
  geom_vline(aes(xintercept=0)) + 
  geom_hline(aes(yintercept=0)) + 
  geom_abline(aes(slope=1,intercept=0)) + 
  geom_point(aes(shape=as.factor(color))) + 
  geom_text_repel(data = . %>% filter(color != 5), aes(label=Pathway), size=3.5, max.overlaps = 100) + 
  geom_text_repel(data = . %>% filter(color == 5), aes(label=Pathway), size=3.5, max.overlaps = 100,
                  arrow=arrow(length=unit(.01,"npc")), box.padding = .8, point.padding = .5) + 
  theme_bw()+ 
  theme(legend.position='none', 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(size=16),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14)) +
  scale_colour_manual(values = c("5" = "red", "4" = "grey40", "3" = "grey40", "1" = "grey40","2" = "grey40")) + 
  labs(x='AAC-based -log10(P-value)', y='Model-based -log10(P-value)',
       title='Estimated significance of pathway regulation')
ggsave(plot=pp, file.path(output_dir, 'pathways.pdf'),width=9,height=9,units='in')
```
